---
title: "test for linear"
author: "Wai"
date: "2024-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing package

```{r}
library(tidyverse)
```

# Importing EXTENDAim1 dataset

```{r}
SCDKAPAim1 <- read_csv("data/SCDKAPAim1.csv")
```

# Combining variable values (scales) that attribute to respective attitude. 

```{r}
sum_all_var <- SCDKAPAim1 %>% 
  mutate(sum_positive = gladmed_ng + friends_ng + satiscare_ng + empathy_ng,
         sum_negative = overreport_ng + failtocom_ng + abusedrugs_ng + manipu_ng + drugseek_ng + frustrate_ng,
         sum_concerns = reqnarc_ng + comfort_ng + disputestaff_ng + ringsbell_ng,
         sum_redflag = changebehav_ng + signout2_ng + tamperpca_ng) %>% 
  select(sum_positive, sum_negative, sum_concerns, sum_redflag, record_id)
```

# Using scales package for linear transformation

```{r}
library(scales)
```


# Linear transformation of combined attitude scales 

## sum_positive: transforming scale from __4 - 20__ to scale __0 - 100__
## sum_negative: transforming scale from __6 - 30__ to scale __0 - 100__
## sum_concerns: transforming scale from __4 - 24__ to scale __0 - 100__
## sum_redflag: transforming scale from __3 - 18__ to scale __0 - 100__

```{r}

id <- sum_all_var$record_id

linear_scale1 <- round(rescale(
  sum_all_var$sum_positive,
  to = c(0,100),
  from = c(4,20)
))

linear_scale2 <- round(rescale(
  sum_all_var$sum_negative,
  to = c(0, 100),
  from = c(6,30)
))

linear_scale3 <- round(rescale(
  sum_all_var$sum_concerns,
  to = c(0, 100),
  from = c(4,24)
))

linear_scale4 <- round(rescale(
  sum_all_var$sum_redflag,
  to = c(0, 100),
  from = c(3,18)
))
                                   
```

# Creating new dataset from the outputs of transformed variables

```{r}
sum_all_var_l <- data.frame(
  record_id = id,
  sum_positive_l = linear_scale1,
  sum_negative_l = linear_scale2,
  sum_concerns_l = linear_scale3,
  sum_redflag_l = linear_scale4
)
```


```{r}
library(writexl)
```

# Exporting dataset to compare with the dataset with original scale

```{r}
write_xlsx(sum_all_var_l, "sum_all_var_l.xlsx")
```

# Exporting dataset with original scale

```{r}
write_xlsx(sum_all_var, "sum_all_var.xlsx")
```

