---
title: "EXTENDAim1 table 3"
author: "Wai"
date: "2024-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages for analysis

```{r}
library(tidyverse)
library(psych)
library(survival)
```
# Importing dataset

```{r}
SCDKAPAim1 <- read_csv("data/SCDKAPAim1.csv")
```
# This is the data analysis for SCDKAP Aim1 Table 3 (attitudes)

# Note: Attitude scores will undergo linear transformation to place all scores on a 0-100 scale. But we do not know the transformation method yet, and hence, for the time being, scores are being calculated based on original scores.

# Checking normality of data distribution before conducting analysis for table 3: attitude scores

## by adding all variables up that attribute to a specific attitude (e.g negative attitude). This will create new variable (column namely sum_negative, sum_positive, sum_concerns, sum_redflag) in which the values are the total sum of all variables contributing to a specific attitude. The new dataframe name will be __sum_all_var__.

```{r}
sum_all_var <- SCDKAPAim1 %>% 
  mutate(sum_positive = gladmed_ng + friends_ng + satiscare_ng + empathy_ng,
         sum_negative = overreport_ng + failtocom_ng + abusedrugs_ng + manipu_ng + drugseek_ng + frustrate_ng,
         sum_concerns = reqnarc_ng + comfort_ng + disputestaff_ng + ringsbell_ng,
         sum_redflag = changebehav_ng + signout2_ng + tamperpca_ng)

# After creating new variables and data frame, we check the data distribution as follows;

sum_all_var %>% 
  ggplot(aes(x = sum_positive)) +
  geom_histogram()

sum_all_var %>% 
  ggplot(aes(x = sum_negative)) +
  geom_histogram()

sum_all_var %>% 
  ggplot(aes(x = sum_concerns)) +
  geom_histogram()

sum_all_var %>% 
  ggplot(aes(x = sum_redflag)) +
  geom_histogram()

# default bins = 30 was used as the probability of each value is between 0 - 30.
```

## Checking normal distribution with Shapiro test

```{r}
shapiro.test(sum_all_var$sum_positive)
shapiro.test(sum_all_var$sum_negative)
shapiro.test(sum_all_var$sum_concerns)
shapiro.test(sum_all_var$sum_redflag)

```

## checking normal distribution by Kurtosis test

```{r}
kurtosi(sum_all_var$sum_positive, na.rm = TRUE)

kurtosi(sum_all_var$sum_negative, na.rm = TRUE)

kurtosi(sum_all_var$sum_concerns, na.rm = TRUE)

kurtosi(sum_all_var$sum_redflag, na.rm = TRUE)
```

## Checking normal distribution by skewness

```{r}

skew(sum_all_var$sum_positive, na.rm = TRUE)

skew(sum_all_var$sum_negative, na.rm = TRUE)

skew(sum_all_var$sum_concerns, na.rm = TRUE)

skew(sum_all_var$sum_redflag, na.rm = TRUE)

```

Based on the results of histogram, shapiro test, kurtosis and skewness tests, it is confirmed that data are __not__ normally distributed.

Therefore, we will report median/IQR and do the Kruskal Wallis Test.


# Calculating for table (3): mean/sd/median/IQR/range for total scores and stratified by specific attitude

## total scores

```{r}
total_score_pos <- sum_all_var %>% # Negative attitude
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_pos = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_pos = quantile(sum_positive, 0.75, na.rm = TRUE),
            IQR_neg = IQR(sum_positive, na.rm = TRUE))
total_score_pos


total_score_neg <- sum_all_var %>% # Negative attitude
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE),
            IQR_neg = IQR(sum_negative, na.rm = TRUE))
total_score_neg


total_score_con <- sum_all_var %>% # Negative attitude
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_con = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_con = quantile(sum_concerns, 0.75, na.rm = TRUE),
            IQR_con = IQR(sum_concerns, na.rm = TRUE))
total_score_con


total_score_red <- sum_all_var %>% # Negative attitude
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_red = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_red = quantile(sum_redflag, 0.75, na.rm = TRUE),
            IQR_red = IQR(sum_redflag, na.rm = TRUE))
total_score_red

```

## Calculating median/IQR for attitude variables grouping by Age

```{r}
age_pos <- sum_all_var %>% # Positive attitude
  group_by(age_ng) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
age_pos


age_neg <- sum_all_var %>% # Negative attitude
  group_by(age_ng) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
age_neg


age_con <- sum_all_var %>% # Concerns attitude
  group_by(age_ng) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
age_con

age_red <- sum_all_var %>% # Redflag attitude
  group_by(age_ng) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
age_red
```


## Calculating median/IQR for attitude variables grouping by profession. __Please be careful__ when checking the prof data. 1 (Physician), 2 (Nurse), 3 (Other).

```{r}

prof_pos <- sum_all_var %>% # Positive attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
prof_pos


prof_neg <- sum_all_var %>% # Negative attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
prof_neg


prof_con <- sum_all_var %>% # Concerns attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
prof_con

prof_red <- sum_all_var %>% # Redflag attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
prof_red
```

## Calculating median/IQR for attitude variables grouping by Patient population. __1 (adult), 2 (paed), 3 (both)__

```{r}
pop_pos <- sum_all_var %>% # Positive attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
pop_pos


pop_neg <- sum_all_var %>% # Negative attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
pop_neg


pop_con <- sum_all_var %>% # Concerns attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
pop_con

pop_red <- sum_all_var %>% # Redflag attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
pop_red
```

## Calculating median/IQR for attitude variables grouping by Practice location

__Primary__

```{r}
loc1_pos <- sum_all_var %>% # Positive attitude
  group_by(practice_location_ng___1) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
loc1_pos


loc1_neg <- sum_all_var %>% # Negative attitude
  group_by(practice_location_ng___1) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
loc1_neg


loc1_con <- sum_all_var %>% # Concerns attitude
  group_by(practice_location_ng___1) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
loc1_con

loc1_red <- sum_all_var %>% # Redflag attitude
  group_by(practice_location_ng___1) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
loc1_red
```

__Secondary__

```{r}
loc2_pos <- sum_all_var %>% # Positive attitude
  group_by(practice_location_ng___2) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
loc2_pos

loc2_neg <- sum_all_var %>% # Negative attitude
  group_by(practice_location_ng___2) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
loc2_neg


loc2_con <- sum_all_var %>% # Concerns attitude
  group_by(practice_location_ng___2) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
loc2_con

loc2_red <- sum_all_var %>% # Redflag attitude
  group_by(practice_location_ng___2) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
loc2_red
```


__Tertiary__ 

```{r}
loc3_pos <- sum_all_var %>% # Positive attitude
  group_by(practice_location_ng___3) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
loc3_pos

loc3_neg <- sum_all_var %>% # Negative attitude
  group_by(practice_location_ng___3) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
loc3_neg


loc3_con <- sum_all_var %>% # Concerns attitude
  group_by(practice_location_ng___3) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
loc3_con

loc3_red <- sum_all_var %>% # Redflag attitude
  group_by(practice_location_ng___3) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
loc3_red
```

__Private Healthcare__

```{r}
loc4_pos <- sum_all_var %>% # Positive attitude
  group_by(practice_location_ng___4) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
loc4_pos

loc4_neg <- sum_all_var %>% # Negative attitude
  group_by(practice_location_ng___4) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
loc4_neg


loc4_con <- sum_all_var %>% # Concerns attitude
  group_by(practice_location_ng___4) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
loc4_con

loc4_red <- sum_all_var %>% # Redflag attitude
  group_by(practice_location_ng___4) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
loc4_red
```

__Other__

```{r}
loc5_pos <- sum_all_var %>% # Positive attitude
  group_by(practice_location_ng___5) %>% 
  summarise(median(sum_positive, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive, 0.75, na.rm = TRUE))
loc5_pos

loc5_neg <- sum_all_var %>% # Negative attitude
  group_by(practice_location_ng___5) %>% 
  summarise(median(sum_negative, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative, 0.75, na.rm = TRUE))
loc5_neg


loc5_con <- sum_all_var %>% # Concerns attitude
  group_by(practice_location_ng___5) %>% 
  summarise(median(sum_concerns, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns, 0.75, na.rm = TRUE))
loc5_con

loc5_red <- sum_all_var %>% # Redflag attitude
  group_by(practice_location_ng___5) %>% 
  summarise(median(sum_redflag, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag, 0.75, na.rm = TRUE))
loc5_red
```

# Kruskal Wallis test by using total sum of all variables attirbuting to one specific attitude if we decide data is __not__ normally distributed.

## Comparison of attitudes stratified by age groups (18-35 | 35 - 65 | 65 years and olders)
 
```{r}
kruskal.test(sum_positive ~ age_ng, data = sum_all_var)

kruskal.test(sum_negative ~ age_ng, data = sum_all_var)

kruskal.test(sum_concerns ~ age_ng, data = sum_all_var)

kruskal.test(sum_redflag ~ age_ng, data = sum_all_var)
```
 
```{r}
library(dunn.test)
```
 
```{r}
dunn.test(sum_all_var$sum_positive, g = sum_all_var$age_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_negative, g = sum_all_var$age_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_concerns, g = sum_all_var$age_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_redflag, g = sum_all_var$age_ng, method = "bonferroni")
```
 
 
 ## Comparison of attitudes stratified by profession (Nurse | Physician | Other)
 
```{r}

kruskal.test(sum_positive ~ profession_ng_up, data = sum_all_var)

kruskal.test(sum_negative ~ profession_ng_up, data = sum_all_var)

kruskal.test(sum_concerns ~ profession_ng_up, data = sum_all_var)

kruskal.test(sum_redflag ~ profession_ng_up, data = sum_all_var)

```
 
```{r}
dunn.test(sum_all_var$sum_positive, g = sum_all_var$profession_ng_up, method = "bonferroni")

dunn.test(sum_all_var$sum_negative, g = sum_all_var$profession_ng_up, method = "bonferroni")

dunn.test(sum_all_var$sum_concerns, g = sum_all_var$profession_ng_up, method = "bonferroni")

dunn.test(sum_all_var$sum_redflag, g = sum_all_var$profession_ng_up, method = "bonferroni")
```
 
 
 
 ## Comparison of attitudes stratified by patient population (Paeds | Adults | Both)
 
```{r}
kruskal.test(sum_positive ~ patient_pop_ng, data = sum_all_var)

kruskal.test(sum_negative ~ patient_pop_ng, data = sum_all_var)

kruskal.test(sum_concerns ~ patient_pop_ng, data = sum_all_var)

kruskal.test(sum_redflag ~ patient_pop_ng, data = sum_all_var)
```
 
```{r}
dunn.test(sum_all_var$sum_positive, g = sum_all_var$patient_pop_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_negative, g = sum_all_var$patient_pop_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_concerns, g = sum_all_var$patient_pop_ng, method = "bonferroni")

dunn.test(sum_all_var$sum_redflag, g = sum_all_var$patient_pop_ng, method = "bonferroni")
```
 
 
# Comparison of attitudes stratified by practice location (primary | secondary | tertiray | private | other)

## Need to discuss with Statistician how we can analyse this data because the data under practice location are not mutually exclusive.
 
```{r}
#kruskal.test(sum_positive ~ , data = sum_all_var)

#kruskal.test(sum_negative ~ , data = sum_all_var)

#kruskal.test(sum_concerns ~ , data = sum_all_var)

#kruskal.test(sum_redflag ~ , data = sum_all_var)
```
 
 
# Cronbach's alpha test for survey questionnaire 

1. Install package "psych"
2. run library(psych)

```{r}
library(psych)
```


* For positive attitude variables

```{r}
alpha_pos <- SCDKAPAim1 %>% 
  select(gladmed_ng, friends_ng, satiscare_ng, empathy_ng)

alpha(alpha_pos, na.rm = TRUE)
```

* For negative attitude variables

```{r}
alpha_neg <- SCDKAPAim1 %>% 
  select(overreport_ng, failtocom_ng, abusedrugs_ng, manipu_ng, drugseek_ng, frustrate_ng)

alpha(alpha_neg, na.rm = TRUE)
```

* For concerns raising behaviors variables

```{r}
alpha_con <- SCDKAPAim1 %>% 
  select(reqnarc_ng, comfort_ng, disputestaff_ng, ringsbell_ng)

alpha(alpha_con, na.rm = TRUE)
```

* For red-flag behaviors variables

```{r}
alpha_red <- SCDKAPAim1 %>% 
  select(changebehav_ng, signout2_ng, tamperpca_ng)

alpha(alpha_red, na.rm = TRUE)
```



