---
title: "SCDKAPa1-Table4(Revised)"
author: "Wai"
date: "2024-07-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading required packages

```{r}
library(tidyverse)
```

# Importing dataset

```{r}
SCDKAPa1 <- read_csv("data/Feb_20_2024_SCDKAPAim1.csv")
```

# Calculating use/do-not-use/NA table

## Create new variable that combines the values of complete adh plus frequntly adh and the values of rarely plus never.

original scale: 1 (never), 2 (rarely), 3 (frequently), 4 (always), 5 (NA)

re-scale: 1 (never & rarely), 2 (frequently & always), 3 (NA)


```{r binary}
binary_adh <- SCDKAPa1 %>% 
  mutate(freqabx_ng = case_when(freqabx_ng %in% c(1,2) ~ 1,
                                freqabx_ng %in% c(3,4) ~ 2,
                                freqabx_ng == 5 ~ 3,
                                TRUE ~ NA),
         freqstopabx_ng = case_when(freqstopabx_ng %in% c(1,2) ~ 1,
                                freqstopabx_ng %in% c(3,4) ~ 2,
                                freqstopabx_ng == 5 ~ 3,
                                TRUE ~ NA),
         freqedpneuvax_ng = case_when(freqedpneuvax_ng %in% c(1,2) ~ 1,
                                freqedpneuvax_ng %in% c(3,4) ~ 2,
                                freqedpneuvax_ng == 5 ~ 3,
                                TRUE ~ NA),
         freqedfever_ng = case_when(freqedfever_ng %in% c(1,2) ~ 1,
                                freqedfever_ng %in% c(3,4) ~ 2,
                                freqedfever_ng == 5 ~ 3,
                                TRUE ~ NA),
         freqcbcretic_ng = case_when(freqcbcretic_ng %in% c(1,2) ~ 1,
                                freqcbcretic_ng %in% c(3,4) ~ 2,
                                freqcbcretic_ng == 5 ~ 3,
                                TRUE ~ NA),
         freqipp_ng = case_when(freqipp_ng %in% c(1,2) ~ 1,
                                freqipp_ng %in% c(3,4) ~ 2,
                                freqipp_ng == 5 ~ 3,
                                TRUE ~ NA),
         consultscd_ng = case_when(consultscd_ng %in% c(1,2) ~ 1,
                                consultscd_ng %in% c(3,4) ~ 2,
                                consultscd_ng == 5 ~ 3,
                                TRUE ~ NA),
         counselmiss_ng = case_when(counselmiss_ng %in% c(1,2) ~ 1,
                                counselmiss_ng %in% c(3,4) ~ 2,
                                counselmiss_ng == 5 ~ 3,
                                TRUE ~ NA),
         educatescd_ng = case_when(educatescd_ng %in% c(1,2) ~ 1,
                                educatescd_ng %in% c(3,4) ~ 2,
                                educatescd_ng == 5 ~ 3,
                                TRUE ~ NA),
         hutherapyadult_ng = case_when(hutherapyadult_ng %in% c(1,2) ~ 1,
                                hutherapyadult_ng %in% c(3,4) ~ 2,
                                hutherapyadult_ng == 5 ~ 3,
                                TRUE ~ NA),
         hutherapypeds_ng = case_when(hutherapypeds_ng %in% c(1,2) ~ 1,
                                hutherapypeds_ng %in% c(3,4) ~ 2,
                                hutherapypeds_ng == 5 ~ 3,
                                TRUE ~ NA),
         disconpreg_ng = case_when(disconpreg_ng %in% c(1,2) ~ 1,
                                disconpreg_ng %in% c(3,4) ~ 2,
                                disconpreg_ng == 5 ~ 3,
                                TRUE ~ NA),
         cbcwithdiff_ng = case_when(cbcwithdiff_ng %in% c(1,2) ~ 1,
                                cbcwithdiff_ng %in% c(3,4) ~ 2,
                                cbcwithdiff_ng == 5 ~ 3,
                                TRUE ~ NA),
         monitorcbc_ng = case_when(monitorcbc_ng %in% c(1,2) ~ 1,
                                monitorcbc_ng %in% c(3,4) ~ 2,
                                monitorcbc_ng == 5 ~ 3,
                                TRUE ~ NA),
         transfus10_ng = case_when(transfus10_ng %in% c(1,2) ~ 1,
                             transfus10_ng %in% c(3,4) ~ 2,
                             transfus10_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         reduchbs_ng = case_when(reduchbs_ng %in% c(1,2) ~ 1,
                             reduchbs_ng %in% c(3,4) ~ 2,
                             reduchbs_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         simpletransfus_ng = case_when(simpletransfus_ng %in% c(1,2) ~ 1,
                             simpletransfus_ng %in% c(3,4) ~ 2,
                             simpletransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         theratransfus_ng = case_when(theratransfus_ng %in% c(1,2) ~ 1,
                             theratransfus_ng %in% c(3,4) ~ 2,
                             theratransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         delaytransfus_ng = case_when(delaytransfus_ng %in% c(1,2) ~ 1,
                             delaytransfus_ng %in% c(3,4) ~ 2,
                             delaytransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         ipptransfus_ng = case_when(ipptransfus_ng %in% c(1,2) ~ 1,
                             ipptransfus_ng %in% c(3,4) ~ 2,
                             ipptransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         rbcantigen_ng = case_when(rbcantigen_ng %in% c(1,2) ~ 1,
                             rbcantigen_ng %in% c(3,4) ~ 2,
                             rbcantigen_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         leukreduc_ng = case_when(leukreduc_ng %in% c(1,2) ~ 1,
                             leukreduc_ng %in% c(3,4) ~ 2,
                             leukreduc_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         chelatthera_ng = case_when(chelatthera_ng %in% c(1,2) ~ 1,
                             chelatthera_ng %in% c(3,4) ~ 2,
                             chelatthera_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         proteinuria_ng = case_when(proteinuria_ng %in% c(1,2) ~ 1,
                             proteinuria_ng %in% c(3,4) ~ 2,
                             proteinuria_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         htn_ng = case_when(htn_ng %in% c(1,2) ~ 1,
                             htn_ng %in% c(3,4) ~ 2,
                             htn_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         bpchild_ng = case_when(bpchild_ng %in% c(1,2) ~ 1,
                             bpchild_ng %in% c(3,4) ~ 2,
                             bpchild_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         extremities_ng = case_when(extremities_ng %in% c(1,2) ~ 1,
                             extremities_ng %in% c(3,4) ~ 2,
                             extremities_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         transcdop_ng = case_when(transcdop_ng %in% c(1,2) ~ 1,
                             transcdop_ng %in% c(3,4) ~ 2,
                             transcdop_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assessresp_ng = case_when(assessresp_ng %in% c(1,2) ~ 1,
                             assessresp_ng %in% c(3,4) ~ 2,
                             assessresp_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         reproriskasses_ng = case_when(reproriskasses_ng %in% c(1,2) ~ 1,
                             reproriskasses_ng %in% c(3,4) ~ 2,
                             reproriskasses_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         adultscdscreen_ng = case_when(adultscdscreen_ng %in% c(1,2) ~ 1,
                             adultscdscreen_ng %in% c(3,4) ~ 2,
                             adultscdscreen_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assessavn_ng = case_when(assessavn_ng %in% c(1,2) ~ 1,
                             assessavn_ng %in% c(3,4) ~ 2,
                             assessavn_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         pregtransfuse_ng = case_when(pregtransfuse_ng %in% c(1,2) ~ 1,
                             pregtransfuse_ng %in% c(3,4) ~ 2,
                             pregtransfuse_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assesssleepbreath_ng = case_when(assesssleepbreath_ng %in% c(1,2) ~ 1,
                             assesssleepbreath_ng %in% c(3,4) ~ 2,
                             assesssleepbreath_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         specialist_ng = case_when(specialist_ng %in% c(1,2) ~ 1,
                             specialist_ng %in% c(3,4) ~ 2,
                             specialist_ng == 5 ~ 3,
                             TRUE ~ NA
                             ))
```


## Now calculate use/do-not-use/NA data, and remove missing number from denominator

### Table 4a Healthcare Provider Use of Health Maintenance Guidelines 

- freqabx_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqabx_ng)) %>% 
  group_by(freqabx_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- freqstopabx_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqstopabx_ng)) %>% 
  group_by(freqstopabx_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- freqedpneuvax_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqedpneuvax_ng)) %>% 
  group_by(freqedpneuvax_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- freqedfever_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqedfever_ng)) %>% 
  group_by(freqedfever_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- freqcbcretic_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqcbcretic_ng)) %>% 
  group_by(freqcbcretic_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- freqipp_ng

```{r}
binary_adh %>% 
  filter(!is.na(freqipp_ng)) %>% 
  group_by(freqipp_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


### Table 4b.2 Healthcare Provider Hydroxyurea Use Guidelines 

- consultscd_ng

```{r}
binary_adh %>% 
  filter(!is.na(consultscd_ng)) %>% 
  group_by(consultscd_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


- counselmiss_ng

```{r}
binary_adh %>% 
  filter(!is.na(counselmiss_ng)) %>% 
  group_by(counselmiss_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


- educatescd_ng

```{r}
binary_adh %>% 
  filter(!is.na(educatescd_ng)) %>% 
  group_by(educatescd_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- hutherapyadult_ng

```{r}
binary_adh %>% 
  filter(!is.na(hutherapyadult_ng)) %>% 
  group_by(hutherapyadult_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- hutherapypeds_ng

```{r}
binary_adh %>% 
  filter(!is.na(hutherapypeds_ng)) %>% 
  group_by(hutherapypeds_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- disconpreg_ng

```{r}
binary_adh %>% 
  filter(!is.na(disconpreg_ng)) %>% 
  group_by(disconpreg_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- cbcwithdiff_ng

```{r}
binary_adh %>% 
  filter(!is.na(cbcwithdiff_ng)) %>% 
  group_by(cbcwithdiff_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- monitorcbc_ng

```{r}
binary_adh %>% 
  filter(!is.na(monitorcbc_ng)) %>% 
  group_by(monitorcbc_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


### Table 4c.2 Healthcare Provider Blood Transfusion Guideline Use

- transfus10_ng

```{r}
binary_adh %>% 
  filter(!is.na(transfus10_ng)) %>% 
  group_by(transfus10_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- reduchbs_ng

```{r}
binary_adh %>% 
  filter(!is.na(reduchbs_ng)) %>% 
  group_by(reduchbs_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- simpletransfus_ng

```{r}
binary_adh %>% 
  filter(!is.na(simpletransfus_ng)) %>% 
  group_by(simpletransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- theratransfus_ng

```{r}
binary_adh %>% 
  filter(!is.na(theratransfus_ng)) %>% 
  group_by(theratransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- delaytransfus_ng

```{r}
binary_adh %>% 
  filter(!is.na(delaytransfus_ng)) %>% 
  group_by(delaytransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- ipptransfus_ng

```{r}
binary_adh %>% 
  filter(!is.na(ipptransfus_ng)) %>% 
  group_by(ipptransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- rbcantigen_ng

```{r}
binary_adh %>% 
  filter(!is.na(rbcantigen_ng)) %>% 
  group_by(rbcantigen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- leukreduc_ng

```{r}
binary_adh %>% 
  filter(!is.na(leukreduc_ng)) %>% 
  group_by(leukreduc_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- chelatthera_ng

```{r}
binary_adh %>% 
  filter(!is.na(chelatthera_ng)) %>% 
  group_by(chelatthera_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### Table 4d. Healthcare Provider Screening Guideline Use

- proteinuria_ng

```{r}
binary_adh %>% 
  filter(!is.na(proteinuria_ng)) %>% 
  group_by(proteinuria_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- htn_ng

```{r}
binary_adh %>% 
  filter(!is.na(htn_ng)) %>% 
  group_by(htn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- bpchild_ng

```{r}
binary_adh %>% 
  filter(!is.na(bpchild_ng)) %>% 
  group_by(bpchild_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- extremities_ng

```{r}
binary_adh %>% 
  filter(!is.na(extremities_ng)) %>% 
  group_by(extremities_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- transcdop_ng

```{r}
binary_adh %>% 
  filter(!is.na(transcdop_ng)) %>% 
  group_by(transcdop_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- assessresp_ng

```{r}
binary_adh %>% 
  filter(!is.na(assessresp_ng)) %>% 
  group_by(assessresp_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- reproriskasses_ng

```{r}
binary_adh %>% 
  filter(!is.na(reproriskasses_ng)) %>% 
  group_by(reproriskasses_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- adultscdscreen_ng

```{r}
binary_adh %>% 
  filter(!is.na(adultscdscreen_ng)) %>% 
  group_by(adultscdscreen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- assessavn_ng

```{r}
binary_adh %>% 
  filter(!is.na(assessavn_ng)) %>% 
  group_by(assessavn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- pregtransfuse_ng

```{r}
binary_adh %>% 
  filter(!is.na(pregtransfuse_ng)) %>% 
  group_by(pregtransfuse_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- assesssleepbreath_ng

```{r}
binary_adh %>% 
  filter(!is.na(assesssleepbreath_ng)) %>% 
  group_by(assesssleepbreath_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

- specialist_ng

```{r}
binary_adh %>% 
  filter(!is.na(specialist_ng)) %>% 
  group_by(specialist_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


## Calculating yes/no data stratified by profession and type of patients

scale: 1 (yes), 0 (no)

profession type     : 1 (physician), 2 (nurse), 3 (other)
patient pop type    : 1 (adults), 2 (peds), 3 (both)

### Table 4b.1 Healthcare Provider Prescription of Hydroxyurea and Hematology Expertise

- hurx_up - Do you prescribe hydroxyurea to individuals with SCD who are eligible for hydroxyurea therapy?

```{r}
SCDKAPa1 %>% 
  group_by(hurx_up, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(hurx_up, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```


- hucollab_ng - Do you work with a hematologist/SCD expert who prescribes hydroxyurea to individuals with SCD who are eligible for hydroxyurea therapy?

```{r}
SCDKAPa1 %>% 
  group_by(hucollab_ng, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(hucollab_ng, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```

### Table 4c.1 Healthcare Provider Guideline Based Blood Transfusion Practices

- ordertransfus_ng - Do you utilize/order blood transfusion (simple and/or exchange) for individuals with SCD?

```{r}
SCDKAPa1 %>% 
  group_by(ordertransfus_ng, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(ordertransfus_ng, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```

- collabtransfus_ng - Do you work with a hematologist/SCD expert who utilizes/orders blood transfusions for individuals with SCD?	

```{r}
SCDKAPa1 %>% 
  group_by(collabtransfus_ng, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(collabtransfus_ng, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```

- xchangetransfus - Do you have access to the equipment and personnel necessary to provide exchange transfusions?	

```{r}
SCDKAPa1 %>% 
  group_by(xchangetransfus, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(xchangetransfus, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```







