---
title: "SCDKAPa1-SuppTable1"
author: "Kirstin"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

Install and Load Packages
```{r}
library(readr)
library(dplyr)
```

1. Import and load data set
```{r}
SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/Duke Grad/IBEMERE/SCD KAP Aim 1/data/Feb_20_2024_SCDKAPAim1.csv")
# SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/SCDKAPAim1.csv") # older dataset version
# View(SCDKAPa1)
```

2. Find the percent reporting use, stratified by rarely, freqeuntly, and always
# Acetaminophen PO - tylenol_po_ng_v2#
```{r}
acetaminophenPO <- SCDKAPa1 %>%
  filter(tylenol_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, tylenol_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[tylenol_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[tylenol_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(tylenol_po_ng_v2 %in% c(1, 2, 3, 4))

print(acetaminophenPO)

# total reporting use
acetaminophenPO <- SCDKAPa1 %>%
  filter(tylenol_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(tylenol_po_ng_v2 == 2),
            count_3 = sum(tylenol_po_ng_v2 == 3),
            count_4 = sum(tylenol_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / 208 * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(acetaminophenPO)
```

# Ibuprofen PO - ibuprofen_po_ng_v2 #
```{r}
IbuprofenPO <- SCDKAPa1 %>%
  filter(ibuprofen_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, ibuprofen_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[ibuprofen_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[ibuprofen_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(ibuprofen_po_ng_v2 %in% c(1, 2, 3, 4))

print(IbuprofenPO)

# total reporting use
IbuprofenPO <- SCDKAPa1 %>%
  filter(ibuprofen_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(ibuprofen_po_ng_v2 == 2),
            count_3 = sum(ibuprofen_po_ng_v2 == 3),
            count_4 = sum(ibuprofen_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(IbuprofenPO)
```

Kertorolac PO - ketorolac_po_ng_v2
```{r}
KertorolacPO <- SCDKAPa1 %>%
  filter(ketorolac_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, ketorolac_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[ketorolac_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[ketorolac_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(ketorolac_po_ng_v2 %in% c(1, 2, 3, 4))

print(KertorolacPO)

# total
KertorolacPO <- SCDKAPa1 %>%
  filter(ketorolac_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(ketorolac_po_ng_v2 == 2),
            count_3 = sum(ketorolac_po_ng_v2 == 3),
            count_4 = sum(ketorolac_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(KertorolacPO)
```

# Kertorolac IV - ketorolac_iv_ng_v2#
```{r}
KertorolacIV <- SCDKAPa1 %>%
  filter(ketorolac_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, ketorolac_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[ketorolac_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[ketorolac_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(ketorolac_iv_ng_v2 %in% c(1, 2, 3, 4))

print(KertorolacIV)

# total
KertorolacIV <- SCDKAPa1 %>%
  filter(ketorolac_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(ketorolac_iv_ng_v2 == 2),
            count_3 = sum(ketorolac_iv_ng_v2 == 3),
            count_4 = sum(ketorolac_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(KertorolacIV)
```

# Other NSAID - othernsaids_surv_ng_v2 #
```{r}
OtherNSAID <- SCDKAPa1 %>%
  filter(othernsaids_surv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, othernsaids_surv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[othernsaids_surv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[othernsaids_surv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(othernsaids_surv_ng_v2 %in% c(1, 2, 3, 4))

print(OtherNSAID)

# total
OtherNSAID <- SCDKAPa1 %>%
  filter(othernsaids_surv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(othernsaids_surv_ng_v2 == 2),
            count_3 = sum(othernsaids_surv_ng_v2 == 3),
            count_4 = sum(othernsaids_surv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(OtherNSAID)
```

# Diphenhydramine PO - benadryl_po_ng_v2 #
```{r}
DiphenhydraminePO <- SCDKAPa1 %>%
  filter(benadryl_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, benadryl_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[benadryl_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[benadryl_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(benadryl_po_ng_v2 %in% c(1, 2, 3, 4))

print(DiphenhydraminePO)

# total
DiphenhydraminePO <- SCDKAPa1 %>%
  filter(benadryl_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(benadryl_po_ng_v2 == 2),
            count_3 = sum(benadryl_po_ng_v2 == 3),
            count_4 = sum(benadryl_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(DiphenhydraminePO)
```

# Diphenhydramine IV - benadryl_iv_ng_v2 #
```{r}
DiphenhydramineIV <- SCDKAPa1 %>%
  filter(benadryl_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, benadryl_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[benadryl_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[benadryl_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(benadryl_iv_ng_v2 %in% c(1, 2, 3, 4))

print(DiphenhydramineIV)

# total
DiphenhydramineIV <- SCDKAPa1 %>%
  filter(benadryl_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(benadryl_iv_ng_v2 == 2),
            count_3 = sum(benadryl_iv_ng_v2 == 3),
            count_4 = sum(benadryl_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(DiphenhydramineIV)
```

# Diphenhydramine SubQ - benadryl_sq_ng_v2 #
```{r}
DiphenhydramineSubQ <- SCDKAPa1 %>%
  filter(benadryl_sq_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, benadryl_sq_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[benadryl_sq_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[benadryl_sq_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(benadryl_sq_ng_v2 %in% c(1, 2, 3, 4))

print(DiphenhydramineSubQ)

# total
DiphenhydramineSubQ <- SCDKAPa1 %>%
  filter(benadryl_sq_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(benadryl_sq_ng_v2 == 2),
            count_3 = sum(benadryl_sq_ng_v2 == 3),
            count_4 = sum(benadryl_sq_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(DiphenhydramineSubQ)
```

# Diphenhydramine PCA - benadryl_pca_ng_v2 #
```{r}
DiphenhydraminePCA <- SCDKAPa1 %>%
  filter(benadryl_pca_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, benadryl_pca_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[benadryl_pca_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[benadryl_pca_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(benadryl_pca_ng_v2 %in% c(1, 2, 3, 4))

print(DiphenhydraminePCA)

# total
DiphenhydraminePCA <- SCDKAPa1 %>%
  filter(benadryl_pca_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(benadryl_pca_ng_v2 == 2),
            count_3 = sum(benadryl_pca_ng_v2 == 3),
            count_4 = sum(benadryl_pca_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(DiphenhydraminePCA)
```

# Other Antihistamine - otherantihist_ng_v2 #
```{r}
OtherAntihistamine <- SCDKAPa1 %>%
  filter(otherantihist_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, otherantihist_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[otherantihist_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[otherantihist_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(otherantihist_ng_v2 %in% c(1, 2, 3, 4))

print(OtherAntihistamine)

# total
OtherAntihistamine <- SCDKAPa1 %>%
  filter(otherantihist_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(otherantihist_ng_v2 == 2),
            count_3 = sum(otherantihist_ng_v2 == 3),
            count_4 = sum(otherantihist_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(OtherAntihistamine)
```

# Morphine PO - morphine_po_ng_v2 #
```{r}
MorphinePO <- SCDKAPa1 %>%
  filter(morphine_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, morphine_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[morphine_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[morphine_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(morphine_po_ng_v2 %in% c(1, 2, 3, 4))

print(MorphinePO)

# total
MorphinePO <- SCDKAPa1 %>%
  filter(morphine_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(morphine_po_ng_v2 == 2),
            count_3 = sum(morphine_po_ng_v2 == 3),
            count_4 = sum(morphine_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MorphinePO)
```

# Morphine IV - morphine_iv_ng_v2 #
```{r}
MorphineIV <- SCDKAPa1 %>%
  filter(morphine_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, morphine_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[morphine_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[morphine_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(morphine_iv_ng_v2 %in% c(1, 2, 3, 4))

print(MorphineIV)

# total
MorphineIV <- SCDKAPa1 %>%
  filter(morphine_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(morphine_iv_ng_v2 == 2),
            count_3 = sum(morphine_iv_ng_v2 == 3),
            count_4 = sum(morphine_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MorphineIV)
```

# Morphine SubQ - morphine_sq_ng_v2 #
```{r}
MorphineSubQ <- SCDKAPa1 %>%
  filter(morphine_sq_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, morphine_sq_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[morphine_sq_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[morphine_sq_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(morphine_sq_ng_v2 %in% c(1, 2, 3, 4))

print(MorphineSubQ)

# total
MorphineSubQ <- SCDKAPa1 %>%
  filter(morphine_sq_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(morphine_sq_ng_v2 == 2),
            count_3 = sum(morphine_sq_ng_v2 == 3),
            count_4 = sum(morphine_sq_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MorphineSubQ)
```

# Morphine PCA - morphine_pca_ng_v2 #
```{r}
MorphinePCA <- SCDKAPa1 %>%
  filter(morphine_pca_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, morphine_pca_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[morphine_pca_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[morphine_pca_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(morphine_pca_ng_v2 %in% c(1, 2, 3, 4))

print(MorphinePCA)

# total
MorphinePCA <- SCDKAPa1 %>%
  filter(morphine_pca_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(morphine_pca_ng_v2 == 2),
            count_3 = sum(morphine_pca_ng_v2 == 3),
            count_4 = sum(morphine_pca_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MorphinePCA)
```

# Hydromorphone PO - dilaudid_po_ng_v2 #
```{r}
HydromorphonePO <- SCDKAPa1 %>%
  filter(dilaudid_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, dilaudid_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[dilaudid_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[dilaudid_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(dilaudid_po_ng_v2 %in% c(1, 2, 3, 4))

print(HydromorphonePO)

# total
HydromorphonePO <- SCDKAPa1 %>%
  filter(dilaudid_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(dilaudid_po_ng_v2 == 2),
            count_3 = sum(dilaudid_po_ng_v2 == 3),
            count_4 = sum(dilaudid_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(HydromorphonePO)
```

# Hydromorphone IV - dilaudid_iv_ng_v2 #
```{r}
HydromorphoneIV <- SCDKAPa1 %>%
  filter(dilaudid_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, dilaudid_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[dilaudid_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[dilaudid_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(dilaudid_iv_ng_v2 %in% c(1, 2, 3, 4))

print(HydromorphoneIV)

# total
HydromorphoneIV <- SCDKAPa1 %>%
  filter(dilaudid_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(dilaudid_iv_ng_v2 == 2),
            count_3 = sum(dilaudid_iv_ng_v2 == 3),
            count_4 = sum(dilaudid_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(HydromorphoneIV)
```

# Hydromorphone SubQ - didaudid_sq_ng_v2 #
```{r}
HydromorphoneSubQ <- SCDKAPa1 %>%
  filter(didaudid_sq_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, didaudid_sq_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[didaudid_sq_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[didaudid_sq_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(didaudid_sq_ng_v2 %in% c(1, 2, 3, 4))

print(HydromorphoneSubQ)

# total
HydromorphoneSubQ <- SCDKAPa1 %>%
  filter(didaudid_sq_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(didaudid_sq_ng_v2 == 2),
            count_3 = sum(didaudid_sq_ng_v2 == 3),
            count_4 = sum(didaudid_sq_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(HydromorphoneSubQ)
```

# Hydromorphone PCA - dilaudid_pca_ng_v2 #
```{r}
HydromorphonePCA <- SCDKAPa1 %>%
  filter(dilaudid_pca_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, dilaudid_pca_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[dilaudid_pca_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[dilaudid_pca_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(dilaudid_pca_ng_v2 %in% c(1, 2, 3, 4))

print(HydromorphonePCA)

# total
HydromorphonePCA <- SCDKAPa1 %>%
  filter(dilaudid_pca_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(dilaudid_pca_ng_v2 == 2),
            count_3 = sum(dilaudid_pca_ng_v2 == 3),
            count_4 = sum(dilaudid_pca_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(HydromorphonePCA)
```

# Oxycodone/oxycontin PO - oxycodone_po_ng_v2 #
```{r}
Oxycodone_oxycontinPO <- SCDKAPa1 %>%
  filter(oxycodone_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, oxycodone_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[oxycodone_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[oxycodone_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(oxycodone_po_ng_v2 %in% c(1, 2, 3, 4))

print(Oxycodone_oxycontinPO)

# total
Oxycodone_oxycontinPO <- SCDKAPa1 %>%
  filter(oxycodone_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(oxycodone_po_ng_v2 == 2),
            count_3 = sum(oxycodone_po_ng_v2 == 3),
            count_4 = sum(oxycodone_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(Oxycodone_oxycontinPO)
```

# Hydrocodone and Acetaminophen PO - norco_po_ng_v2 #
```{r}
Hydrocodone_AcetaminophenPO <- SCDKAPa1 %>%
  filter(norco_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, norco_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[norco_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[norco_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(norco_po_ng_v2 %in% c(1, 2, 3, 4))

print(Hydrocodone_AcetaminophenPO)

# total
Hydrocodone_AcetaminophenPO <- SCDKAPa1 %>%
  filter(norco_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(norco_po_ng_v2 == 2),
            count_3 = sum(norco_po_ng_v2 == 3),
            count_4 = sum(norco_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(Hydrocodone_AcetaminophenPO)
```

# Oxycodone and Acetaminophen PO - percocet_po_ng_v2 #
```{r}
Oxycodone_AcetaminophenPO <- SCDKAPa1 %>%
  filter(percocet_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, percocet_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[percocet_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[percocet_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(percocet_po_ng_v2 %in% c(1, 2, 3, 4))

print(Oxycodone_AcetaminophenPO)

# total
Oxycodone_AcetaminophenPO <- SCDKAPa1 %>%
  filter(percocet_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(percocet_po_ng_v2 == 2),
            count_3 = sum(percocet_po_ng_v2 == 3),
            count_4 = sum(percocet_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(Oxycodone_AcetaminophenPO)
```

# Codeine PO - codeine_po_ng_v2 #
```{r}
CodeinePO <- SCDKAPa1 %>%
  filter(codeine_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, codeine_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[codeine_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[codeine_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(codeine_po_ng_v2 %in% c(1, 2, 3, 4))

print(CodeinePO)

# total
CodeinePO <- SCDKAPa1 %>%
  filter(codeine_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(codeine_po_ng_v2 == 2),
            count_3 = sum(codeine_po_ng_v2 == 3),
            count_4 = sum(codeine_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(CodeinePO)
```

# Codeine IV - codeine_iv_ng_v2 #
```{r}
CodeineIV <- SCDKAPa1 %>%
  filter(codeine_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, codeine_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[codeine_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[codeine_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(codeine_iv_ng_v2 %in% c(1, 2, 3, 4))

print(CodeineIV)

# total
CodeineIV <- SCDKAPa1 %>%
  filter(codeine_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(codeine_iv_ng_v2 == 2),
            count_3 = sum(codeine_iv_ng_v2 == 3),
            count_4 = sum(codeine_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(CodeineIV)
```

# Merperidine PO - demerol_po_ng_v2 #
```{r}
MerperidinePO <- SCDKAPa1 %>%
  filter(demerol_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, demerol_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[demerol_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[demerol_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(demerol_po_ng_v2 %in% c(1, 2, 3, 4))

print(MerperidinePO)

# total
MerperidinePO <- SCDKAPa1 %>%
  filter(demerol_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(demerol_po_ng_v2 == 2),
            count_3 = sum(demerol_po_ng_v2 == 3),
            count_4 = sum(demerol_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MerperidinePO)

```

# Merperidine IV - demerol_iv_ng_v2 #
```{r}
MerperidineIV <- SCDKAPa1 %>%
  filter(demerol_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, demerol_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[demerol_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[demerol_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(demerol_iv_ng_v2 %in% c(1, 2, 3, 4))

print(MerperidineIV)

# total
MerperidineIV <- SCDKAPa1 %>%
  filter(demerol_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(demerol_iv_ng_v2 == 2),
            count_3 = sum(demerol_iv_ng_v2 == 3),
            count_4 = sum(demerol_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MerperidineIV)

```

# Merperidine SubQ - demerol_sq_ng_v2 #
```{r}
MerperidineSubQ <- SCDKAPa1 %>%
  filter(demerol_sq_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, demerol_sq_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[demerol_sq_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[demerol_sq_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(demerol_sq_ng_v2 %in% c(1, 2, 3, 4))

print(MerperidineSubQ)

# total
MerperidineSubQ <- SCDKAPa1 %>%
  filter(demerol_sq_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(demerol_sq_ng_v2 == 2),
            count_3 = sum(demerol_sq_ng_v2 == 3),
            count_4 = sum(demerol_sq_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MerperidineSubQ)

```

# Merperidine PCA - demerol_pca_ng_v2 #
```{r}
MerperidinePCA <- SCDKAPa1 %>%
  filter(demerol_pca_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, demerol_pca_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[demerol_pca_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[demerol_pca_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(demerol_pca_ng_v2 %in% c(1, 2, 3, 4))

print(MerperidinePCA)

# total 
MerperidinePCA <- SCDKAPa1 %>%
  filter(demerol_pca_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(demerol_pca_ng_v2 == 2),
            count_3 = sum(demerol_pca_ng_v2 == 3),
            count_4 = sum(demerol_pca_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MerperidinePCA)

```

# Fentanyl PO - fentanyl_po_ng_v2 #
```{r}
FentanylPO <- SCDKAPa1 %>%
  filter(fentanyl_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, fentanyl_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[fentanyl_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[fentanyl_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(fentanyl_po_ng_v2 %in% c(1, 2, 3, 4))

print(FentanylPO)

# total
FentanylPO <- SCDKAPa1 %>%
  filter(fentanyl_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(fentanyl_po_ng_v2 == 2),
            count_3 = sum(fentanyl_po_ng_v2 == 3),
            count_4 = sum(fentanyl_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(FentanylPO)

```

# Fentanyl IV - fentanyl_iv_ng_v2 #
```{r}
FentanylIV <- SCDKAPa1 %>%
  filter(fentanyl_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, fentanyl_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[fentanyl_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[fentanyl_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(fentanyl_iv_ng_v2 %in% c(1, 2, 3, 4))

print(FentanylIV)

# total
FentanylIV <- SCDKAPa1 %>%
  filter(fentanyl_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(fentanyl_iv_ng_v2 == 2),
            count_3 = sum(fentanyl_iv_ng_v2 == 3),
            count_4 = sum(fentanyl_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(FentanylIV)

```

# Fentanyl PCA - fentanyl_pca_ng_v2 #
```{r}
FentanylPCA <- SCDKAPa1 %>%
  filter(fentanyl_pca_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, fentanyl_pca_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[fentanyl_pca_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[fentanyl_pca_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(fentanyl_pca_ng_v2 %in% c(1, 2, 3, 4))

print(FentanylPCA)

# total
FentanylPCA <- SCDKAPa1 %>%
  filter(fentanyl_pca_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(fentanyl_pca_ng_v2 == 2),
            count_3 = sum(fentanyl_pca_ng_v2 == 3),
            count_4 = sum(fentanyl_pca_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(FentanylPCA)

```

# Methadone PO - methadone_po_ng_v2 #
```{r}
MethadonePO <- SCDKAPa1 %>%
  filter(methadone_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, methadone_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[methadone_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[methadone_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(methadone_po_ng_v2 %in% c(1, 2, 3, 4))

print(MethadonePO)

# total
MethadonePO <- SCDKAPa1 %>%
  filter(methadone_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(methadone_po_ng_v2 == 2),
            count_3 = sum(methadone_po_ng_v2 == 3),
            count_4 = sum(methadone_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MethadonePO)

```

# Methadone IV - methadone_iv_ng_v2 #
```{r}
MethadoneIV <- SCDKAPa1 %>%
  filter(methadone_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, methadone_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[methadone_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[methadone_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(methadone_iv_ng_v2 %in% c(1, 2, 3, 4))

print(MethadoneIV)

# total
MethadoneIV <- SCDKAPa1 %>%
  filter(methadone_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(methadone_iv_ng_v2 == 2),
            count_3 = sum(methadone_iv_ng_v2 == 3),
            count_4 = sum(methadone_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(MethadoneIV)

```

# Other opiate - otheropiate_ng_v2 #
```{r}
Otheropiate <- SCDKAPa1 %>%
  filter(otheropiate_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, otheropiate_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[otheropiate_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[otheropiate_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(otheropiate_ng_v2 %in% c(1, 2, 3, 4))

print(Otheropiate)

# total
Otheropiate <- SCDKAPa1 %>%
  filter(otheropiate_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(otheropiate_ng_v2 == 2),
            count_3 = sum(otheropiate_ng_v2 == 3),
            count_4 = sum(otheropiate_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(Otheropiate)

```

# Tramadol PO - tramadol_po_ng_v2 #
```{r}
TramadolPO <- SCDKAPa1 %>%
  filter(tramadol_po_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, tramadol_po_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[tramadol_po_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[tramadol_po_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(tramadol_po_ng_v2 %in% c(1, 2, 3, 4))

print(TramadolPO)

# total
TramadolPO <- SCDKAPa1 %>%
  filter(tramadol_po_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(tramadol_po_ng_v2 == 2),
            count_3 = sum(tramadol_po_ng_v2 == 3),
            count_4 = sum(tramadol_po_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(TramadolPO)
```

# Tramadol IV - tramadol_iv_ng_v2 #
```{r}
TramadolIV <- SCDKAPa1 %>%
  filter(tramadol_iv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, tramadol_iv_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[tramadol_iv_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[tramadol_iv_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(tramadol_iv_ng_v2 %in% c(1, 2, 3, 4))

print(TramadolIV)

# total
TramadolIV <- SCDKAPa1 %>%
  filter(tramadol_iv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(tramadol_iv_ng_v2 == 2),
            count_3 = sum(tramadol_iv_ng_v2 == 3),
            count_4 = sum(tramadol_iv_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(TramadolIV)
```

# Other medication - othermed_ng_v2 #
```{r}
Othermedication <- SCDKAPa1 %>%
  filter(othermed_ng_v2 %in% c(1, 2, 3, 4)) %>%
  group_by(profession_ng_up, othermed_ng_v2) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(profession_ng_up) %>%
  mutate(total = sum(count)) %>%
  mutate(percent = count / total * 100) %>%
  mutate(totalreportinguse = sum(count[othermed_ng_v2 %in% c(2, 3, 4)]),
       totalnouse = sum(count[othermed_ng_v2 == 1]),
       totalpart = sum(count),
       percentwuse = totalreportinguse / totalpart * 100,
       percentwoutuse = totalnouse / totalpart * 100) %>%
  filter(othermed_ng_v2 %in% c(1, 2, 3, 4))

print(Othermedication)

# total
Othermedication <- SCDKAPa1 %>%
  filter(othermed_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(othermed_ng_v2 == 2),
            count_3 = sum(othermed_ng_v2 == 3),
            count_4 = sum(othermed_ng_v2 == 4),
            total_participants = n()) %>%
  mutate(total_percent = (count_2 + count_3 + count_4) / total_participants * 100,
         percent_2 = count_2 / total_participants * 100,
         percent_3 = count_3 / total_participants * 100,
         percent_4 = count_4 / total_participants * 100)

print(Othermedication)
```

## Create new categories for other responses ##
Create new variable summarizing categories discussed in other text, which have significant numbers:

1. Pentazocine
```{r}
# Vector of record_ids want to code as 1 (N = 42) - reported pentazocine in other text box for "otheropiate_ng_v2"
pentazocine_used_inotherop <- c(1, 7, 10, 16, 27, 29, 42, 45, 51, 60, 61, 64, 86, 127, 151, 186, 220, 222, 223, 225, 238, 284, 293, 297, 299, 335, 350, 352, 376, 382, 386, 388,399,400,423,438,458,466,474, 510, 518, 529)  # included all record_ids that noted pentazocine as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$pentazocine_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% pentazocine_used_inotherop, 1, 0)

# Filter the data frame
freqeuncy_pentazocine <- SCDKAPa1 %>% #37
  filter(pentazocine_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(otheropiate_ng_v2 %in% c(1, 2, 3, 4)) %>%
  summarise(count_1 = sum(otheropiate_ng_v2 == 1),
            count_2 = sum(otheropiate_ng_v2 == 2),
            count_3 = sum(otheropiate_ng_v2 == 3),
            count_4 = sum(otheropiate_ng_v2 == 4))

freqeuncy_pentazocine

## ADD TWO VALUES ##

# Vector of record_ids want to code as 1 (N = 10) - - reported pentazocine in other text box for "othernsaids_surv_ng_v2"
pentazocine_used_inothernsaid<-c(193, 194, 204, 208, 209, 328, 347, 364, 424, 467)

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$pentazocine_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% pentazocine_used_inothernsaid, 1, 0)

# Filter the data frame
freqeuncy_pentazocine <- SCDKAPa1 %>% # 32
  filter(pentazocine_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(othernsaids_surv_ng_v2 %in% c(1, 2, 3, 4)) %>%
  summarise(count_2 = sum(othernsaids_surv_ng_v2 == 2),
            count_3 = sum(othernsaids_surv_ng_v2 == 3),
            count_4 = sum(othernsaids_surv_ng_v2 == 4))

freqeuncy_pentazocine
```

2. Chlopheniramine / Piriton
```{r}
# Vector of record_ids want to code as 1 (N = 27) - reported Chlopheniramine / Piriton in other text box for "otherantihist_ng_v2"
piriton_inotheranti <- c(27, 101, 186, 304, 304, 333, 344, 400, 423, 7, 63, 151, 166, 217, 195, 220, 250, 293, 310, 328, 293, 310, 328, 332, 362, 424, 500)  # included all record_ids that noted Chlopheniramine / Piriton as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$piriton_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% piriton_inotheranti, 1, 0)

#Double check dataset ensuring sample size of n = 30
piriton_responses <- filter(SCDKAPa1, piriton_po_ng_v2 == 1)
piritonandotherresponse <- loratidine_responses[, c("piriton_po_ng_v2", "otherantihist_ng_v2")]
print(piritonandotherresponse)

# Filter the data frame
freqeuncy_piriton <- SCDKAPa1 %>% #37
  filter(piriton_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(otherantihist_ng_v2 %in% c(1, 2, 3, 4)) %>%
  summarise(count_1 = sum(otherantihist_ng_v2 == 1),
            count_2 = sum(otherantihist_ng_v2 == 2),
            count_3 = sum(otherantihist_ng_v2 == 3),
            count_4 = sum(otherantihist_ng_v2 == 4))

freqeuncy_piriton
```

3. Loratidine
```{r}
# Vector of record_ids want to code as 1 (N = 30) - reported Chlopheniramine / Piriton in other text box for "otherantihist_ng_v2"
loratidine_inotheranti <- c(25, 34, 145, 147, 151, 170, 191, 194, 195, 214, 268, 291, 314, 322, 328, 314, 322, 328, 352, 370, 374, 376, 382, 388, 399, 458, 463, 467, 482, 504, 519, 530, 531)  # included all record_ids that noted Chlopheniramine / Piriton as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$loratidine_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% loratidine_inotheranti, 1, 0)

#Double check dataset ensuring sample size of n = 30
loratidine_responses <- filter(SCDKAPa1, loratidine_po_ng_v2 == 1)
loratidineandotherresponse <- loratidine_responses[, c("loratidine_po_ng_v2", "otherantihist_ng_v2")]
print(loratidineandotherresponse)

# Filter the data frame
freqeuncy_loratidine <- SCDKAPa1 %>% #37
  filter(loratidine_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(otherantihist_ng_v2 %in% c(1, 2, 3, 4)) %>%
  summarise(count_1 = sum(otherantihist_ng_v2 == 1),
            count_2 = sum(otherantihist_ng_v2 == 2),
            count_3 = sum(otherantihist_ng_v2 == 3),
            count_4 = sum(otherantihist_ng_v2 == 4))

freqeuncy_loratidine
```

4. Diclofenac
```{r}
# Vector of record_ids want to code as 1 (N = 73) - reported Diclofenac in other text box for "othernsaids_surv_ng_v2"
diclofenac_inothernsaid <- c(1, 7, 8, 10, 12, 16, 25, 27, 32, 33, 34, 37, 43, 45, 47, 51, 54, 55, 61, 63, 64, 101, 136, 142, 145, 151, 161, 166, 186, 195, 199, 222, 223, 232, 238, 304, 310, 313, 328, 333, 350, 352, 359, 370, 376, 379, 382,385, 386, 388, 399, 400, 417, 423, 428, 438, 460, 461, 463, 466, 474, 481,490, 493, 508, 510, 522, 530)  # included all record_ids that noted Diclofenac as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$diclofenac_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% diclofenac_inothernsaid, 1, 0)

# Filter the data frame
freqeuncy_diclofenac <- SCDKAPa1 %>% #37
  filter(diclofenac_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(othernsaids_surv_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(othernsaids_surv_ng_v2 == 2),
            count_3 = sum(othernsaids_surv_ng_v2 == 3),
            count_4 = sum(othernsaids_surv_ng_v2 == 4))

freqeuncy_diclofenac

## ADD TWO VALUES ##

# Vector of record_ids want to code as 1 (N = 73) - reported Diclofenac in other text box for "other_med_ng_v2"
diclofenac_inothermed <- c(395, 398, 407, 346, 316)  # included all record_ids that noted Diclofenac as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$diclofenac_po_ng_v2 <- ifelse(SCDKAPa1$record_id %in% diclofenac_inothermed, 1, 0)

# Filter the data frame
freqeuncy_diclofenac <- SCDKAPa1 %>% #37
  filter(diclofenac_po_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(othermed_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(othermed_ng_v2 == 2),
            count_3 = sum(othermed_ng_v2 == 3),
            count_4 = sum(othermed_ng_v2 == 4))

freqeuncy_diclofenac
```

Vitamins (e.g., Multivitamin, Folic Acid, Haemantinics)
```{r}
# Vector of record_ids want to code as 1 (N = 20) - reported Diclofenac in other text box for "other_med_ng_v2"
vitamins_inothermed <- c(508, 1, 176, 64, 145, 194, 199, 204, 223, 232, 352, 438, 474, 481, 482, 492, 530, 531, 250, 518)  # included all record_ids that noted Diclofenac as another medication they used in practice

# Create a new variable where individuals with specific record_ids are coded as 1
SCDKAPa1$vitamins_ng_v2 <- ifelse(SCDKAPa1$record_id %in% vitamins_inothermed, 1, 0)

# Filter the data frame
freqeuncy_vitamins <- SCDKAPa1 %>% #37
  filter(vitamins_ng_v2 == 1) %>%
  group_by(profession_ng_up) %>%
  filter(othermed_ng_v2 %in% c(2, 3, 4)) %>%
  summarise(count_2 = sum(othermed_ng_v2 == 2),
            count_3 = sum(othermed_ng_v2 == 3),
            count_4 = sum(othermed_ng_v2 == 4))

freqeuncy_vitamins
```


