---
title: "Knowledge Code - SCDKAP Aim 1"
author: "Kirstin"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

Install and Load Packages
```{r}
library(readr)
library(dplyr)
```

1. Import and load data set
```{r}
SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/Duke Grad/IBEMERE/SCD KAP Aim 1/data/Feb_20_2024_SCDKAPAim1.csv")
# SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/SCDKAPAim1.csv") # older dataset version
# View(SCDKAPa1)
```

2. Create variable(s) for number of questions correct
Create variable for the total number of questions correct (out of 18). For each answer the participant answers correctly, the value of one is added to the "totalcorrect" variable.
```{r}
# Create a new variable "totalcorrect" and initialize it with zeros
SCDKAPa1$totalcorrect <- 0

# Increment "totalcorrect" based on conditions
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$patho_ng == "c", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$complscdpeds_ng == "a", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$acutechestpres_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$investcause_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$manifescdpeds_ng == "a", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$hemorstroke_ng == "2", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$ironover_ng == "2", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$acutechronpain_ng == "1", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$goldstand_ng == "a", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$contransaids_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$indicmetha_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$insomantx_ng == "b", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$hemo_ng == "2", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$longshortpain_ng == "1", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$edvisit_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$socialinfluence_ng == "d", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$psychosocial_ng == "a", 1, 0)
SCDKAPa1$totalcorrect <- SCDKAPa1$totalcorrect + ifelse(SCDKAPa1$addictionadapt_ng == "2", 1, 0)

# Convert the total number correct for all participants to the total percent correct
SCDKAPa1$total_percentcorrect <- (SCDKAPa1$totalcorrect / 18) * 100

# View(SCDKAPa1)
```

Create variable for the complication questions correct (out of 8). For each answer the participant answers correctly, the value of one is added to the "compcorrect" variable.
```{r}
# Create a new variable "compcorrect" and initialize it with zeros
SCDKAPa1$compcorrect <- 0

# Increment "compcorrect" based on conditions
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$patho_ng == "c", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$complscdpeds_ng == "a", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$acutechestpres_ng == "d", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$investcause_ng == "d", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$manifescdpeds_ng == "a", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$hemorstroke_ng == "2", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$ironover_ng == "2", 1, 0)
SCDKAPa1$compcorrect <- SCDKAPa1$compcorrect + ifelse(SCDKAPa1$acutechronpain_ng == "1", 1, 0)

# Convert the number of compcorrect for all participants to the total percent of compcorrect
SCDKAPa1$comp_percentcorrect <- (SCDKAPa1$compcorrect / 8) * 100

# View(SCDKAPa1)
```

Create variable for management questions correct (out of 6). For each answer the participant answers correctly, the value of one is added to the "managecorrect" variable.
```{r}
# Create a new variable "compcorrect" and initialize it with zeros
SCDKAPa1$managecorrect <- 0

SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$goldstand_ng == "a", 1, 0)
SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$contransaids_ng == "d", 1, 0)
SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$indicmetha_ng == "d", 1, 0)
SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$insomantx_ng == "b", 1, 0)
SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$hemo_ng == "2", 1, 0)
SCDKAPa1$managecorrect <- SCDKAPa1$managecorrect + ifelse(SCDKAPa1$longshortpain_ng == "1", 1, 0)

# Convert the number of managecorrect for all participants to the total percent of managecorrect
SCDKAPa1$manage_percentcorrect <- (SCDKAPa1$managecorrect / 6) * 100

# View(SCDKAPa1)
```

Create variable for bps questions correct (out of 4). For each answer the participant answers correctly, the value of one is added to the "bpscorrect" variable.
```{r}
# Create a new variable "bpscorrect" and initialize it with zeros
SCDKAPa1$bpscorrect <- 0

SCDKAPa1$bpscorrect <- SCDKAPa1$bpscorrect + ifelse(SCDKAPa1$edvisit_ng == "d", 1, 0)
SCDKAPa1$bpscorrect <- SCDKAPa1$bpscorrect + ifelse(SCDKAPa1$socialinfluence_ng == "d", 1, 0)
SCDKAPa1$bpscorrect <- SCDKAPa1$bpscorrect + ifelse(SCDKAPa1$psychosocial_ng == "a", 1, 0)
SCDKAPa1$bpscorrect <- SCDKAPa1$bpscorrect + ifelse(SCDKAPa1$addictionadapt_ng == "2", 1, 0)

# Convert the number of bpscorrect for all participants to the total percent of bpscorrect
SCDKAPa1$bps_percentcorrect <- (SCDKAPa1$bpscorrect / 6) * 100

# View(SCDKAPa1)
```

3. Check distribution of values / normality
Number Correct
```{r}
# total
hist(SCDKAPa1$totalcorrect, main = "Histogram of Total Correct") # Not normal
shapiro.test(SCDKAPa1$totalcorrect)

# comp
hist(SCDKAPa1$compcorrect, main = "Histogram of Complication Correct") # Not normal
shapiro.test(SCDKAPa1$compcorrect)

# manage
hist(SCDKAPa1$managecorrect, main = "Histogram of Management Correct") # Not normal
shapiro.test(SCDKAPa1$managecorrect)

# bps
hist(SCDKAPa1$bpscorrect, main = "Histogram of Biopsychosocial Correct") # Not normal
shapiro.test(SCDKAPa1$bpscorrect)
```

Percent Correct
```{r}
# total
hist(SCDKAPa1$total_percentcorrect, main = "Histogram of Total Correct") # Not normal
shapiro.test(SCDKAPa1$total_percentcorrect)

# comp
hist(SCDKAPa1$comp_percentcorrect, main = "Histogram of Complication Correct") # Not normal
shapiro.test(SCDKAPa1$comp_percentcorrect)

# manage
hist(SCDKAPa1$manage_percentcorrect, main = "Histogram of Management Correct") # Not normal
shapiro.test(SCDKAPa1$manage_percentcorrect)

# bps
hist(SCDKAPa1$bps_percentcorrect, main = "Histogram of Biopsychosocial Correct") # Not normal
shapiro.test(SCDKAPa1$bps_percentcorrect)
```

4. Calculate table values
### POPULATION TOTAL PERCENT CORRECT ###
Total
```{r}
# Median and IQR for total sample size
total_median_correct <- median(SCDKAPa1$total_percentcorrect, na.rm = TRUE)
total_q1 <- quantile(SCDKAPa1$total_percentcorrect, probs = 0.25, na.rm = TRUE)
total_q3 <- quantile(SCDKAPa1$total_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(paste("Total Median:", total_median_correct))
print(paste("Total 25% IQR:", total_q1))
print(paste("Total 75% IQR:", total_q3))

# Confidence Intervals
t.test(SCDKAPa1$total_percentcorrect)
```

Complications - Total
```{r}
# Complications Median and IQR for total sample size
comptotal_median_correct <- median(SCDKAPa1$comp_percentcorrect, na.rm = TRUE)
total_q1 <- quantile(SCDKAPa1$comp_percentcorrect, probs = 0.25, na.rm = TRUE)
total_q3 <- quantile(SCDKAPa1$comp_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(paste("Total Median:", comptotal_median_correct))
print(paste("Total 25% IQR:", total_q1))
print(paste("Total 75% IQR:", total_q3))
```

Management - Total
```{r}
# Managment Median and IQR for total sample size
managetotal_median_correct <- median(SCDKAPa1$manage_percentcorrect, na.rm = TRUE)
total_q1 <- quantile(SCDKAPa1$manage_percentcorrect, probs = 0.25, na.rm = TRUE)
total_q3 <- quantile(SCDKAPa1$manage_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(paste("Total Median:", managetotal_median_correct))
print(paste("Total 25% IQR:", total_q1))
print(paste("Total 75% IQR:", total_q3))
```

Biopsychosocial - Total
```{r}
# Biopsychosocial Median and IQR for total sample size
bpstotal_median_correct <- median(SCDKAPa1$bps_percentcorrect, na.rm = TRUE)
total_q1 <- quantile(SCDKAPa1$bps_percentcorrect, probs = 0.25, na.rm = TRUE)
total_q3 <- quantile(SCDKAPa1$bps_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(paste("Total Median:", bpstotal_median_correct))
print(paste("Total 25% IQR:", total_q1))
print(paste("Total 75% IQR:", total_q3))
```

### BY PROFESSION ###
Total Correct
```{r}
# Median and IQR for each group
totalmedian_iqr_by_group <- SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

# Print the median (and IQR) number correct
print(totalmedian_iqr_by_group)

# PValues - Perform the Kruskal-Wallis test
kruskal.test(total_percentcorrect ~ profession_ng_up, data = SCDKAPa1)

# Confidence Intervals of Total % correct for each profession category
ci_by_professiongroup <- SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_professiongroup
```

Complications
```{r}
# Median and IQR for each group
compmedian_iqr_by_group <- SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

# Median and IQR for total sample size
totalcomp_median_correct <- median(SCDKAPa1$comp_percentcorrect, na.rm = TRUE)
comptotal_q1 <- quantile(SCDKAPa1$comp_percentcorrect, probs = 0.25, na.rm = TRUE)
comptotal_q3 <- quantile(SCDKAPa1$comp_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(compmedian_iqr_by_group)
print(paste("Total Median:", totalcomp_median_correct))
print(paste("Total 25% IQR:", comptotal_q1))
print(paste("Total 75% IQR:", comptotal_q3))
```

Management
```{r}
# Median and IQR for each group
managemedian_iqr_by_group <- SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

# Median and IQR for total sample size
totalmanage_median_correct <- median(SCDKAPa1$manage_percentcorrect, na.rm = TRUE)
managetotal_q1 <- quantile(SCDKAPa1$manage_percentcorrect, probs = 0.25, na.rm = TRUE)
managetotal_q3 <- quantile(SCDKAPa1$manage_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(managemedian_iqr_by_group)
print(paste("Total Median:", totalmanage_median_correct))
print(paste("Total 25% IQR:", managetotal_q1))
print(paste("Total 75% IQR:", managetotal_q3))
```

Biopsychosocial
```{r}
# Median and IQR for each group
bpsmedian_iqr_by_group <- SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

# Median and IQR for total sample size
totalbps_median_correct <- median(SCDKAPa1$bps_percentcorrect, na.rm = TRUE)
bpstotal_q1 <- quantile(SCDKAPa1$bps_percentcorrect, probs = 0.25, na.rm = TRUE)
bpstotal_q3 <- quantile(SCDKAPa1$bps_percentcorrect, probs = 0.75, na.rm = TRUE)

# Print the median (and IQR) number correct
print(bpsmedian_iqr_by_group)
print(paste("Total Median:", totalbps_median_correct))
print(paste("Total 25% IQR:", bpstotal_q1))
print(paste("Total 75% IQR:", bpstotal_q3))
```

### BY AGE ###
Total Correct
```{r}
# Re-categorize age group
SCDKAPa1 <- SCDKAPa1 %>%
  dplyr::mutate(age_ng = case_when( #age category
    age_ng == 2 ~ 1, # Recode 18 - 35 as 1
    age_ng %in% c(3, 4) ~ 2, # Recode 36 - 65+ as 2
    TRUE ~  age_ng # Keep other values unchanged
  ))

# Median and IQR for each age group - total
totalmedian_iqr_by_age <- SCDKAPa1 %>%
  group_by(age_ng) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_age

# PValues - Perform the Kruskal-Wallis test
kruskal.test(total_percentcorrect ~ age_ng, data = SCDKAPa1)

# Confidence Intervals of Total % correct for each age category
ci_by_agegroup <- SCDKAPa1 %>%
  group_by(age_ng) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_agegroup
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_age <- SCDKAPa1 %>%
  group_by(age_ng) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_age
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_age <- SCDKAPa1 %>%
  group_by(age_ng) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_age
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_age <- SCDKAPa1 %>%
  group_by(age_ng) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_age
```

### BY PATIENT POPULATION ###
Total Correct
```{r}
# Median and IQR for each age group - total
totalmedian_iqr_by_patpop <- SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_patpop

# PValues - Perform the Kruskal-Wallis test
kruskal.test(total_percentcorrect ~ patient_pop_ng, data = SCDKAPa1)

# Confidence Intervals of Total % correct for each patient population
ci_by_patpop <- SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_patpop
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_patpop <- SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_patpop
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_patpop <- SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_patpop
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_patpop <- SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_patpop
```

### BY PRACTICE LOCATION ###
# PRIMARY #
Total Correct
```{r}
# Median and IQR for each age group - total
totalmedian_iqr_by_primpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___1) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_primpracloc

# Confidence Intervals of Total % correct for each practice location
ci_by_primpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___1) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_primpracloc
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_primpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___1) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_primpracloc
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_primpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___1) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_primpracloc
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_primpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___1) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_primpracloc
```

# SECONDARY #
Total Correct
```{r}
# Median and IQR for each age group - total
totalmedian_iqr_by_secpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___2) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_secpracloc

# Confidence Intervals of Total % correct for each practice location
ci_by_secpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___2) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_secpracloc
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_secpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___2) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_secpracloc
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_secpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___2) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_secpracloc
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_secpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___2) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_secpracloc
```

# TERTIARY #
Total Correct
```{r}
# Median and IQR for each age group - total
totalmedian_iqr_by_tertpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___3) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_tertpracloc

# Confidence Intervals of Total % correct for each practice location
ci_by_tertpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___3) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_tertpracloc
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_tertpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___3) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_tertpracloc
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_tertpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___3) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_tertpracloc
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_tertpracloc <- SCDKAPa1 %>%
  group_by(practice_location_ng___3) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_tertpracloc
```

# PRIVATE And OTHER# 
Edited to combine private health care category and other healthcare category
Total Correct
```{r}
# Create a new variable 'private_and_or_otherlocation'
SCDKAPa1$private_and_or_otherlocation <- ifelse(SCDKAPa1$practice_location_ng___4 == 1 | SCDKAPa1$practice_location_ng___5 == 1, 1, 0)
# View(SCDKAPa1)

# Median and IQR for each age group - total
totalmedian_iqr_by_private_and_or_otherlocation <- SCDKAPa1 %>%
  group_by(private_and_or_otherlocation) %>%
  summarize(
    median_correct = median(total_percentcorrect, na.rm = TRUE),
    q1 = quantile(total_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(total_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

totalmedian_iqr_by_private_and_or_otherlocation

# Confidence Intervals of Total % correct for each practice location
ci_by_private_and_or_otherlocation <- SCDKAPa1 %>%
  group_by(private_and_or_otherlocation) %>%
  summarize(
    ci_lower = t.test(total_percentcorrect)$conf.int[1],
    ci_upper = t.test(total_percentcorrect)$conf.int[2]
  )

ci_by_private_and_or_otherlocation
```

Complications
```{r}
# Median and IQR for each age group - complications
compmedian_iqr_by_private_and_or_otherlocation <- SCDKAPa1 %>%
  group_by(private_and_or_otherlocation) %>%
  summarize(
    median_correct = median(comp_percentcorrect, na.rm = TRUE),
    q1 = quantile(comp_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(comp_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

compmedian_iqr_by_private_and_or_otherlocation
```

Management
```{r}
# Median and IQR for each age group - management
managemedian_iqr_by_private_and_or_otherlocation <- SCDKAPa1 %>%
  group_by(private_and_or_otherlocation) %>%
  summarize(
    median_correct = median(manage_percentcorrect, na.rm = TRUE),
    q1 = quantile(manage_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(manage_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

managemedian_iqr_by_private_and_or_otherlocation
```

Biopsychosocial
```{r}
# Median and IQR for each age group - bps
bpsmedian_iqr_by_private_and_or_otherlocation <- SCDKAPa1 %>%
  group_by(private_and_or_otherlocation) %>%
  summarize(
    median_correct = median(bps_percentcorrect, na.rm = TRUE),
    q1 = quantile(bps_percentcorrect, probs = 0.25, na.rm = TRUE),
    q3 = quantile(bps_percentcorrect, probs = 0.75, na.rm = TRUE)
  )

bpsmedian_iqr_by_private_and_or_otherlocation
```

5. Conduct Wilcoxon rank-sum test test to compare percent correct within groups (comparing total percent correct) because the Kruskal-Wallis test yeilded significant results across all groups. Used a Wilcoxon rank-sum test (rather than PostHoc TukeyHSD) to compare significant differences between medians within groups.
### AGE - WILCOXONRANKSUM ###
```{r}
# Create pairwise comparisons between levels of "age_ng"
age_levels <- unique(SCDKAPa1$age_ng)

# Perform pairwise Wilcoxon rank-sum test for each pair of age groups
for (i in 1:(length(age_levels) - 1)) {
  for (j in (i + 1):length(age_levels)) {
    age_group1 <- age_levels[i]
    age_group2 <- age_levels[j]
    
    # Subset data for the two groups
    group1 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$age_ng == age_group1]
    group2 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$age_ng == age_group2]
    
    # Check if the groups are not empty
    if (length(group1) == 0 | length(group2) == 0) {
      cat("Warning: One or more groups is empty.\n")
      next  # Skip to the next iteration if one or more groups is empty
    }
    
    # Perform Wilcoxon rank-sum test
    test_result <- wilcox.test(group1, group2)
    
    # Calculate medians
    median_group1 <- median(group1, na.rm = TRUE)
    median_group2 <- median(group2, na.rm = TRUE)
    
    # Check for NA values in medians
    if (is.na(median_group1) | is.na(median_group2)) {
      cat("Warning: One or more medians is NA.\n")
      next  # Skip to the next iteration if one or more medians is NA
    }
    
    # Print the results
    cat("Comparison between", age_group1, "and", age_group2, ":\n")
    cat("Median difference:", median_group1 - median_group2, "\n")
    print(test_result)
    cat("\n")
  }
}
```

### PROFESSION - WILCOXONRANKSUM ###
```{r}
# Create pairwise comparisons between levels of "age_ng"
profession_levels <- unique(SCDKAPa1$profession_ng_up)

# Perform pairwise Wilcoxon rank-sum test for each pair of age groups
for (i in 1:(length(profession_levels) - 1)) {
  for (j in (i + 1):length(profession_levels)) {
    profession_group1 <- profession_levels[i]
    profession_group2 <- profession_levels[j]
    
    # Subset data for the two groups
    group1 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$profession_ng_up == profession_group1]
    group2 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$profession_ng_up == profession_group2]
    
    # Check if the groups are not empty
    if (length(group1) == 0 | length(group2) == 0) {
      cat("Warning: One or more groups is empty.\n")
      next  # Skip to the next iteration if one or more groups is empty
    }
    
    # Perform Wilcoxon rank-sum test
    test_result <- wilcox.test(group1, group2)
    
    # Calculate medians
    median_group1 <- median(group1, na.rm = TRUE)
    median_group2 <- median(group2, na.rm = TRUE)
    
    # Check for NA values in medians
    if (is.na(median_group1) | is.na(median_group2)) {
      cat("Warning: One or more medians is NA.\n")
      next  # Skip to the next iteration if one or more medians is NA
    }
    
    # Print the results
    cat("Comparison between", profession_group1, "and", profession_group2, ":\n")
    cat("Median difference:", median_group1 - median_group2, "\n")
    print(test_result)
    cat("\n")
  }
}
```


### PATIENT POPULATION - WILCOXONRANKSUM ###
```{r}
# Create pairwise comparisons between levels of "age_ng"
patpop_levels <- unique(SCDKAPa1$patient_pop_ng)

# Perform pairwise Wilcoxon rank-sum test for each pair of age groups
for (i in 1:(length(patpop_levels) - 1)) {
  for (j in (i + 1):length(patpop_levels)) {
    patpop_group1 <- patpop_levels[i]
    patpop_group2 <- patpop_levels[j]
    
    # Subset data for the two groups
    group1 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$patient_pop_ng == patpop_group1]
    group2 <- SCDKAPa1$total_percentcorrect[SCDKAPa1$patient_pop_ng == patpop_group2]
    
    # Check if the groups are not empty
    if (length(group1) == 0 | length(group2) == 0) {
      cat("Warning: One or more groups is empty.\n")
      next  # Skip to the next iteration if one or more groups is empty
    }
    
    # Perform Wilcoxon rank-sum test
    test_result <- wilcox.test(group1, group2)
    
    # Calculate medians
    median_group1 <- median(group1, na.rm = TRUE)
    median_group2 <- median(group2, na.rm = TRUE)
    
    # Check for NA values in medians
    if (is.na(median_group1) | is.na(median_group2)) {
      cat("Warning: One or more medians is NA.\n")
      next  # Skip to the next iteration if one or more medians is NA
    }
    
    # Print the results
    cat("Comparison between", patpop_group1, "and", patpop_group2, ":\n")
    cat("Median difference:", median_group1 - median_group2, "\n")
    print(test_result)
    cat("\n")
  }
}
```


## Determine Cronbach alphas for knowledge table ##
```{r}
# install.packages("psych")
library(psych)
```

1. For Complications
```{r}
# Method #1
alpha_complications <- SCDKAPa1 %>% 
  select(patho_ng, complscdpeds_ng, acutechestpres_ng, investcause_ng, manifescdpeds_ng, hemorstroke_ng, ironover_ng, acutechronpain_ng)

alpha(alpha_pos, na.rm = TRUE)

# Method #2
complication_ca <- c("patho_ng", "complscdpeds_ng", "acutechestpres_ng", 
                         "investcause_ng", "manifescdpeds_ng", "hemorstroke_ng", 
                         "ironover_ng", "acutechronpain_ng")

assesscomplications <- SCDKAPa1[, complication_ca]

alpha(assesscomplications)
```










