---
title: "EXTENDAim1 table 3"
author: "Wai"
date: "2024-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages for analysis

```{r}
library(tidyverse)
library(psych)
```
# Importing datasets

```{r}
sum_all_var <- read_csv("data/sum_all_var_l.csv")
original <- read_csv("data/Feb_20_2024_SCDKAPAim1.csv")
```


# Joining datasets 

```{r}
SCDKAPa1 <- original %>% 
  left_join(sum_all_var, by = "record_id")
```

Now we got the final dataset that can be used for the data analysis of SCDKAP Aim1 Table 3 (attitudes). Attitude scales have been changed on a scale of 0 to 100. 


# Checking normality of data distribution before conducting analysis for table 3: attitude scores

```{r}

SCDKAPa1 %>% 
  ggplot(aes(x = sum_positive_l)) +
  geom_histogram()

SCDKAPa1 %>% 
  ggplot(aes(x = sum_negative_l)) +
  geom_histogram()

SCDKAPa1 %>% 
  ggplot(aes(x = sum_concerns_l)) +
  geom_histogram()

SCDKAPa1 %>% 
  ggplot(aes(x = sum_redflag_l)) +
  geom_histogram()

# default bins = 30 was used as the probability of each value is between 0 - 30.
```

## Checking normal distribution with Shapiro test

```{r}
shapiro.test(SCDKAPa1$sum_positive_l)
shapiro.test(SCDKAPa1$sum_negative_l)
shapiro.test(SCDKAPa1$sum_concerns_l)
shapiro.test(SCDKAPa1$sum_redflag_l)

```

## checking normal distribution by Kurtosis test

```{r}
kurtosi(SCDKAPa1$sum_positive_l, na.rm = TRUE)

kurtosi(SCDKAPa1$sum_negative_l, na.rm = TRUE)

kurtosi(SCDKAPa1$sum_concerns_l, na.rm = TRUE)

kurtosi(SCDKAPa1$sum_redflag_l, na.rm = TRUE)
```

## Checking normal distribution by skewness

```{r}

skew(SCDKAPa1$sum_positive_l, na.rm = TRUE)

skew(SCDKAPa1$sum_negative_l, na.rm = TRUE)

skew(SCDKAPa1$sum_concerns_l, na.rm = TRUE)

skew(SCDKAPa1$sum_redflag_l, na.rm = TRUE)

```

Based on the results of histogram, shapiro test, kurtosis and skewness tests, it is confirmed that data are __not__ normally distributed.

Therefore, we will report median/IQR and do the Kruskal Wallis Test.


# Calculating for table (3): mean/sd/median/IQR/range for total scores and stratified by specific attitude

## Total scores

```{r}
total_score_pos <- SCDKAPa1 %>% # Positive attitude
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_pos = quantile(sum_positive_l, 0.25, na.rm = TRUE),
            quantile_75_pos = quantile(sum_positive_l, 0.75, na.rm = TRUE),
            IQR_pos = IQR(sum_positive_l, na.rm = TRUE))
total_score_pos


total_score_neg <- SCDKAPa1 %>% # Negative attitude
  summarise(median(sum_negative_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative_l, 0.75, na.rm = TRUE),
            IQR_neg = IQR(sum_negative_l, na.rm = TRUE))
total_score_neg


total_score_con <- SCDKAPa1 %>% # Negative attitude
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_con = quantile(sum_concerns_l, 0.25, na.rm = TRUE),
            quantile_75_con = quantile(sum_concerns_l, 0.75, na.rm = TRUE),
            IQR_con = IQR(sum_concerns_l, na.rm = TRUE))
total_score_con


total_score_red <- SCDKAPa1 %>% # Negative attitude
  summarise(median(sum_redflag_l, na.rm = TRUE),
            quantile_25_red = quantile(sum_redflag_l, 0.25, na.rm = TRUE),
            quantile_75_red = quantile(sum_redflag_l, 0.75, na.rm = TRUE),
            IQR_red = IQR(sum_redflag_l, na.rm = TRUE))
total_score_red

```

## Calculating median/IQR for attitude variables grouping by Age

```{r}

age_number <- SCDKAPa1 %>% 
  group_by(age_ng) %>% 
  count()
age_number

age_pos <- SCDKAPa1 %>% # Positive attitude
  group_by(age_ng) %>% 
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive_l, 0.75, na.rm = TRUE))
age_pos


age_neg <- SCDKAPa1 %>% # Negative attitude
  group_by(age_ng) %>% 
  summarise(median(sum_negative_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative_l, 0.75, na.rm = TRUE))
age_neg


age_con <- SCDKAPa1 %>% # Concerns attitude
  group_by(age_ng) %>% 
  summarise(median(sum_concerns_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns_l, 0.75, na.rm = TRUE))
age_con

age_red <- SCDKAPa1 %>% # Redflag attitude
  group_by(age_ng) %>% 
  summarise(median(sum_redflag_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag_l, 0.75, na.rm = TRUE))
age_red
```


## Calculating median/IQR for attitude variables grouping by profession. __Please be careful__ when checking the prof data. 1 (Physician), 2 (Nurse), 3 (Other).

```{r}

prof_number <- SCDKAPa1 %>% 
  group_by(profession_ng_up) %>% 
  count()
prof_number


prof_pos <- SCDKAPa1 %>% # Positive attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive_l, 0.75, na.rm = TRUE))
prof_pos


prof_neg <- SCDKAPa1 %>% # Negative attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_negative_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative_l, 0.75, na.rm = TRUE))
prof_neg


prof_con <- SCDKAPa1 %>% # Concerns attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_concerns_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns_l, 0.75, na.rm = TRUE))
prof_con

prof_red <- SCDKAPa1 %>% # Redflag attitude
  group_by(profession_ng_up) %>% 
  summarise(median(sum_redflag_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag_l, 0.75, na.rm = TRUE))
prof_red
```

## Calculating median/IQR for attitude variables grouping by Patient population. __1 (adult), 2 (paed), 3 (both)__

```{r}

pop_number <- SCDKAPa1 %>% 
  group_by(patient_pop_ng) %>% 
  count()
pop_number

pop_pos <- SCDKAPa1 %>% # Positive attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive_l, 0.75, na.rm = TRUE))
pop_pos


pop_neg <- SCDKAPa1 %>% # Negative attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_negative_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative_l, 0.75, na.rm = TRUE))
pop_neg


pop_con <- SCDKAPa1 %>% # Concerns attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_concerns_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns_l, 0.75, na.rm = TRUE))
pop_con

pop_red <- SCDKAPa1 %>% # Redflag attitude
  group_by(patient_pop_ng) %>% 
  summarise(median(sum_redflag_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag_l, 0.75, na.rm = TRUE))
pop_red
```


## Calculating median/IQR for attitude variables grouping by number of patients seen 

(1) 0-5, (2) 6-10, (3) 10-15, (4) 16-20, (5) 20 or more


```{r}
ptseen_number <- SCDKAPa1 %>% 
  group_by(numscdpt_ng) %>% 
  count()
ptseen_number

ptseen_pos <- SCDKAPa1 %>% # Positive attitude
  group_by(numscdpt_ng) %>% 
  summarise(median(sum_positive_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_positive_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_positive_l, 0.75, na.rm = TRUE))
ptseen_pos


ptseen_neg <- SCDKAPa1 %>% # Negative attitude
  group_by(numscdpt_ng) %>% 
  summarise(median(sum_negative_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_negative_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_negative_l, 0.75, na.rm = TRUE))
ptseen_neg


ptseen_con <- SCDKAPa1 %>% # Concerns attitude
  group_by(numscdpt_ng) %>% 
  summarise(median(sum_concerns_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_concerns_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_concerns_l, 0.75, na.rm = TRUE))
ptseen_con

ptseen_red <- SCDKAPa1 %>% # Redflag attitude
  group_by(numscdpt_ng) %>% 
  summarise(median(sum_redflag_l, na.rm = TRUE),
            quantile_25_neg = quantile(sum_redflag_l, 0.25, na.rm = TRUE),
            quantile_75_neg = quantile(sum_redflag_l, 0.75, na.rm = TRUE))
ptseen_red
```


# Kruskal Wallis test by using total sum of all variables attirbuting to one specific attitude if we decide data is __not__ normally distributed.

## Comparison of attitudes stratified by age groups (18-35 | 35 - 65 | 65 years and olders)
 
```{r}
kruskal.test(sum_positive_l ~ age_ng, data = SCDKAPa1)

kruskal.test(sum_negative_l ~ age_ng, data = SCDKAPa1)

kruskal.test(sum_concerns_l ~ age_ng, data = SCDKAPa1)

kruskal.test(sum_redflag_l ~ age_ng, data = SCDKAPa1)
```
 
```{r}
library(dunn.test)
```
 
 
## Comparison of attitudes stratified by profession (Nurse | Physician | Other)
 
```{r}

kruskal.test(sum_positive_l ~ profession_ng_up, data = SCDKAPa1)

kruskal.test(sum_negative_l ~ profession_ng_up, data = SCDKAPa1)

kruskal.test(sum_concerns_l ~ profession_ng_up, data = SCDKAPa1)

kruskal.test(sum_redflag_l ~ profession_ng_up, data = SCDKAPa1)

```
 
 
## Comparison of attitudes stratified by patient population (Adults | Paeds | Both)
 
```{r}
kruskal.test(sum_positive_l ~ patient_pop_ng, data = SCDKAPa1)

kruskal.test(sum_negative_l ~ patient_pop_ng, data = SCDKAPa1)

kruskal.test(sum_concerns_l ~ patient_pop_ng, data = SCDKAPa1)

kruskal.test(sum_redflag_l ~ patient_pop_ng, data = SCDKAPa1)
```
 
```{r}
dunn.test(SCDKAPa1$sum_positive_l, g = SCDKAPa1$patient_pop_ng, method = "bonferroni")

dunn.test(SCDKAPa1$sum_negative_l, g = SCDKAPa1$patient_pop_ng, method = "bonferroni")

dunn.test(SCDKAPa1$sum_concerns_l, g = SCDKAPa1$patient_pop_ng, method = "bonferroni")

dunn.test(SCDKAPa1$sum_redflag_l, g = SCDKAPa1$patient_pop_ng, method = "bonferroni")
```

## Comparison of attitudes stratified by number of patients seen (0-5 | 6-10 | 10-15 | 16-20 | 20 or more)
 
```{r}
kruskal.test(sum_positive_l ~ numscdpt_ng, data = SCDKAPa1)

kruskal.test(sum_negative_l ~ numscdpt_ng, data = SCDKAPa1)

kruskal.test(sum_concerns_l ~ numscdpt_ng, data = SCDKAPa1)

kruskal.test(sum_redflag_l ~ numscdpt_ng, data = SCDKAPa1)
```
 




