---
title: "table X correct answer knowledge question"
author: "Wai"
date: "2024-06-18"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```


```{r}
SCDKAPa1 <- read_csv("data/Feb_20_2024_SCDKAPAim1.csv")
```

# Which of the following pathophysiologic mechanisms are associated with SCD? Ans: e

```{r}
SCDKAPa1 %>% 
  group_by(patho_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


# Which of the following complications is not common among children with SCD? Ans: e

```{r}
SCDKAPa1 %>% 
  group_by(complscdpeds_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Acute chest syndrome may be associated with which of the following presentations? Ans: d

```{r}
SCDKAPa1 %>% 
  group_by(acutechestpres_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Which of the following pain symptoms should warrant further investigation for the cause? Ans: d

```{r}
SCDKAPa1 %>% 
  group_by(investcause_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Which of the following painful conditions is frequently the initial manifestation of SCD in children? Ans: a 

```{r}
SCDKAPa1 %>% 
  group_by(manifescdpeds_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Which of the following approaches to analgesic management is considered the gold standard? Ans: a

```{r}
SCDKAPa1 %>% 
  group_by(goldstand_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Potential reasons for repeat ED visits include all of the following except? Ans: d

```{r}
SCDKAPa1 %>% 
  group_by(edvisit_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# List the most common contraindication to NSAIDs for patients with SCD? Ans: d

```{r}
SCDKAPa1 %>% 
  group_by(contransaids_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Methadone may be indicated for which of the following patients? Ans: 

```{r}
SCDKAPa1 %>% 
  group_by(indicmetha_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Using opioids to treat insomnia, anxiety, or for some other purpose than treating pain defines which of the following? Ans: b

```{r}
SCDKAPa1 %>% 
  group_by(insomantx_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```
# Which of the following social issues may influence patients with SCD? Ans: d

```{r}
SCDKAPa1 %>% 
  group_by(socialinfluence_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Which of the following psychological issues are not common among patients with SCD? Ans: a 

```{r}
SCDKAPa1 %>% 
  group_by(psychosocial_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Acute hemorrhagic stroke is more common in children than adults? Ans: b (false)

```{r}
SCDKAPa1 %>% 
  group_by(hemorstroke_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Iron overload is common in all adults with SCD? Ans: b (false)

```{r}
SCDKAPa1 %>% 
  group_by(ironover_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Patients with a hemoglobin of < 5 g/dL should always be transfused? Ans: b (false)

```{r}
SCDKAPa1 %>% 
  group_by(hemo_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Many patients with SCD experience both acute and chronic pain? Ans: a (true)

```{r}
SCDKAPa1 %>% 
  group_by(acutechronpain_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Long- and short-acting opioids have a role in the management of SCD for patients with chronic pain? Ans: a (true)

```{r}
SCDKAPa1 %>% 
  group_by(longshortpain_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

# Addiction is a state of adaptation in which exposure to a drug induces changes that result in a diminution of one or more of the drug's effects over time? Ans: b (false)

```{r}
SCDKAPa1 %>% 
  group_by(addictionadapt_ng, profession_ng_up) %>% 
  summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```





