---
title: "SCDKAPa1-Table4"
author: "Kirstin"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
---

Install and Load Packages
```{r}
library(readr)
library(dplyr)
library(tidyverse)
library(table1)
```

## Table 4a and 4b - Kirstin ##
1. Import and load data set
```{r}
#SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/Duke Grad/IBEMERE/SCD KAP Aim 1/data/Feb_20_2024_SCDKAPAim1.csv")
# SCDKAPa1 <- read_csv("/Users/kirstinwest/Desktop/SCDKAPAim1.csv") # older dataset version

SCDKAPa1 <- read_csv("data/Feb_20_2024_SCDKAPAim1.csv") #Uploaded dataset to check the code error
```

2. Ensure appropriate variable character (as factor OR as numeric) - Table 4a and 4b
```{r}
# as.factor
## -> Health Maintenance
SCDKAPa1$freqabx_ng<-as.factor(SCDKAPa1$freqabx_ng)
SCDKAPa1$freqstopabx_ng<-as.factor(SCDKAPa1$freqstopabx_ng)
SCDKAPa1$freqedpneuvax_ng<-as.factor(SCDKAPa1$freqedpneuvax_ng)
SCDKAPa1$freqedfever_ng<-as.factor(SCDKAPa1$freqedfever_ng)
SCDKAPa1$freqcbcretic_ng<-as.factor(SCDKAPa1$freqcbcretic_ng)
SCDKAPa1$freqipp_ng<-as.factor(SCDKAPa1$freqipp_ng)

## -> Hydroxyurea
SCDKAPa1$hurx_up<-as.factor(SCDKAPa1$hurx_up)
SCDKAPa1$hucollab_ng<-as.factor(SCDKAPa1$hucollab_ng)
SCDKAPa1$consultscd_ng<-as.factor(SCDKAPa1$consultscd_ng)
SCDKAPa1$counselmiss_ng<-as.factor(SCDKAPa1$counselmiss_ng)
SCDKAPa1$educatescd_ng<-as.factor(SCDKAPa1$educatescd_ng)
SCDKAPa1$hutherapyadult_ng<-as.factor(SCDKAPa1$hutherapyadult_ng)
SCDKAPa1$hutherapypeds_ng<-as.factor(SCDKAPa1$hutherapypeds_ng)
SCDKAPa1$disconpreg_ng<-as.factor(SCDKAPa1$disconpreg_ng)
SCDKAPa1$cbcwithdiff_ng<-as.factor(SCDKAPa1$cbcwithdiff_ng)
SCDKAPa1$monitorcbc_ng<-as.factor(SCDKAPa1$monitorcbc_ng)
```

3. Relabel variables for table
```{r}
# Health Maintenance
SCDKAPa1$freqabx_ng <- 
  factor(SCDKAPa1$freqabx_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$freqstopabx_ng <- 
  factor(SCDKAPa1$freqstopabx_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$freqedpneuvax_ng <- 
  factor(SCDKAPa1$freqedpneuvax_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$freqedfever_ng <- 
  factor(SCDKAPa1$freqedfever_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$freqcbcretic_ng <- 
  factor(SCDKAPa1$freqcbcretic_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$freqipp_ng <- 
  factor(SCDKAPa1$freqipp_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

# Hydroxyurea
SCDKAPa1$hurx_up <- 
  factor(SCDKAPa1$hurx_up, levels=c("1", "0"),
         labels=c("Completely adhere / yes",
                  "Never adhere / no"))

SCDKAPa1$hucollab_ng <- 
  factor(SCDKAPa1$hucollab_ng, levels=c("1", "0"),
         labels=c("Completely adhere / yes",
                  "Never adhere / no"))

SCDKAPa1$consultscd_ng <- 
  factor(SCDKAPa1$consultscd_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$counselmiss_ng <- 
  factor(SCDKAPa1$counselmiss_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$educatescd_ng <- 
  factor(SCDKAPa1$educatescd_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$hutherapyadult_ng <- 
  factor(SCDKAPa1$hutherapyadult_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$hutherapypeds_ng <- 
  factor(SCDKAPa1$hutherapypeds_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$disconpreg_ng <- 
  factor(SCDKAPa1$disconpreg_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$cbcwithdiff_ng <- 
  factor(SCDKAPa1$cbcwithdiff_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))

SCDKAPa1$monitorcbc_ng <- 
  factor(SCDKAPa1$monitorcbc_ng, levels=c("4","3", "2", "1", "5"),
         labels=c("Completely adhere / always",
                  "Freqeuntly adhere",
                  "Rarely adhere",
                  "Never adhere",
                  "NA"))
```

4. Generate Table 4a and 4b (Kirstin)
```{r}
# Table 4a: Health Maintenance
table1(~ freqabx_ng + freqstopabx_ng + freqedpneuvax_ng + freqedfever_ng + freqcbcretic_ng + freqipp_ng, data = SCDKAPa1, droplevels = TRUE, overall = "Total")

# Table 4b
table1(~ hurx_up + hucollab_ng + consultscd_ng + counselmiss_ng + educatescd_ng + hutherapyadult_ng + hutherapypeds_ng + disconpreg_ng + cbcwithdiff_ng + monitorcbc_ng, data = SCDKAPa1, droplevels = TRUE, overall = "Total")
```

Stratify binary (Yes adhere versus No adhere) variables by profession type and patient population
```{r}
# Do you prescribe hydroxyurea to individuals with SCD who are eligible for hydroxyurea therapy?
SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    yes = sum(hurx_up == 1),
    no = sum(hurx_up == 0)
  )

SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    yes = sum(hurx_up == 1),
    no = sum(hurx_up == 0)
  )

# Do you work with a hematologist/SCD expert who prescribes hydroxyurea to individuals with SCD who are eligible for hydroxyurea therapy? 
SCDKAPa1 %>%
  group_by(profession_ng_up) %>%
  summarize(
    yes = sum(hucollab_ng == 1),
    no = sum(hucollab_ng == 0)
  )

SCDKAPa1 %>%
  group_by(patient_pop_ng) %>%
  summarize(
    yes = sum(hucollab_ng == 1),
    no = sum(hucollab_ng == 0)
  )
```


hurx_up
hucollab_ng

## Table 4c. Healthcare Provider Adherence to Guideline Based Blood Transfusion Recommendations - Wai

Section Header: Please indicate how frequently you (or you and your SCD expert colleague) do the following:

scale: 1 (yes), 2 (no)

scale: 1 (never), 2 (rarely), 3 (frequently), 4 (always)

profession type     : 1 (physician), 2 (nurse), 3 (other)
patient pop type    : 1 (adults), 2 (peds), 3 (both)

```{r}
SCDKAPa1 %>% 
  select(record_id, ordertransfus_ng:chelatthera_ng)
```


### ordertransfus_ng - Do you utilize/order blood transfusion (simple and/or exchange) for individuals with SCD?

```{r}
SCDKAPa1 %>% 
  group_by(ordertransfus_ng, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(ordertransfus_ng, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```

### collabtransfus_ng - Do you work with a hematologist/SCD expert who utilizes/orders blood transfusions for individuals with SCD?	

```{r}
SCDKAPa1 %>% 
  group_by(collabtransfus_ng, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(collabtransfus_ng, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```

### xchangetransfus - Do you have access to the equipment and personnel necessary to provide exchange transfusions?	

```{r}
SCDKAPa1 %>% 
  group_by(xchangetransfus, profession_ng_up) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(profession_ng_up) %>% 
  mutate(percentage = round(n/sum(n)*100,1))


SCDKAPa1 %>% 
  group_by(xchangetransfus, patient_pop_ng) %>% 
   summarise(
    n = n(),
    .groups = "drop"
  ) %>% 
  group_by(patient_pop_ng) %>% 
  mutate(percentage = round(n/sum(n)*100,1))
```


### transfus10_ng - Order preoperative simple blood transfusion with goal hemoglobin of 10 g/dL /or patient specific hemoglobin goal	

```{r}
SCDKAPa1 %>% 
  group_by(transfus10_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


### reduchbs_ng - Provide prophylactic blood transfusions for maximum reduction of hemoglobin S (< 30%) in individuals with HbSS	

```{r}
SCDKAPa1 %>% 
  group_by(reduchbs_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### simpletransfus_ng - Order simple transfusion for uncomplicated vaso-occlusive episode	

```{r}
SCDKAPa1 %>% 
  group_by(simpletransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### theratransfus_ng - Provide therapeutic blood transfusions for acute sickle cell disease complications	

```{r}
SCDKAPa1 %>% 
  group_by(theratransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### delaytransfus_ng - Delay transfusion while seeking cause of acute, severe anemia	

```{r}
SCDKAPa1 %>% 
  group_by(delaytransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### ipptransfus_ng - Create an individualized patient plan for the use of simple and/or exchange transfusion as part of disease management	

```{r}
SCDKAPa1 %>% 
  group_by(ipptransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### rbcantigen_ng - Match for minor red blood cell antigens 

```{r}
SCDKAPa1 %>% 
  group_by(rbcantigen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### leukreduc_ng - Use pre-storage leukoreduction or bedside white blood cell filtration

```{r}
SCDKAPa1 %>% 
  group_by(leukreduc_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### chelatthera_ng - Order chelation therapy

```{r}
SCDKAPa1 %>% 
  group_by(chelatthera_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


## Table 4d.  Healthcare Provider Adherence to screening recommendations

```{r}
SCDKAPa1 %>% 
  select(record_id, proteinuria_ng:specialist_ng)
```


### proteinuria_ng - Screen for proteinuria by at least age 10

```{r}
SCDKAPa1 %>% 
  group_by(proteinuria_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### htn_ng - Screen for hypertension in adults (SBP≥130, DBP≥80)

```{r}
SCDKAPa1 %>% 
  group_by(htn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### bpchild_ng - Monitor BP in children

```{r}
SCDKAPa1 %>% 
  group_by(bpchild_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### extremities_ng - Examine extremities and initiate treatment for active or healed ulcers

```{r}
SCDKAPa1 %>% 
  group_by(extremities_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### transcdop_ng - Conduct annual transcranial doppler from ages 2 to 16 years according to STOP study methods (specific to HbSS, HbSβ0 thalassemia) 

```{r}
SCDKAPa1 %>% 
  group_by(transcdop_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assessresp_ng - Assess for signs and symptoms of respiratory problems like asthma, COPD, restrictive lung disease or refer to an appropriate specialist

```{r}
SCDKAPa1 %>% 
  group_by(assessresp_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### reproriskasses_ng - Conduct reproductive risk assessment, educational and health promotion counseling or refer to specialist for women and men of childbearing age or refer to an appropriate specialist 

```{r}
SCDKAPa1 %>% 
  group_by(reproriskasses_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### adultscdscreen_ng - Refer male and female partners for sickle cell screening 

```{r}
SCDKAPa1 %>% 
  group_by(adultscdscreen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assessavn_ng - Screen all individuals with SCD and intermittent or chronic hip pain for avascular necrosis (history, physical exam, imaging) 

```{r}
SCDKAPa1 %>% 
  group_by(assessavn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### pregtransfuse_ng - Screen women who have been transfused and are pregnant for red cell alloantibodies 

```{r}
SCDKAPa1 %>% 
  group_by(pregtransfuse_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assesssleepbreath_ng - Assess for signs and symptoms of sleep-disordered breathing like sleep apnea or refer to an appropriate specialist 

```{r}
SCDKAPa1 %>% 
  group_by(assesssleepbreath_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### specialist_ng - Refer to appropriate specialist for specific disease complication or co-morbidity treatment

```{r}
SCDKAPa1 %>% 
  group_by(specialist_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```



# Calculating binary variable for adherence 

## Table 4c (binary)

### Create new variable that combines the values of complete adh plus frequntly adh and the values of rarely plus never.

scale: 1 (never), 2 (rarely), 3 (frequently), 4 (always)

rescale: 1 (never & rarely), 2 (frequently & always), 3 (NA)


```{r binary}
binary_adh <- SCDKAPa1 %>% 
  mutate(transfus10_ng = case_when(transfus10_ng %in% c(1,2) ~ 1,
                             transfus10_ng %in% c(3,4) ~ 2,
                             transfus10_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         reduchbs_ng = case_when(reduchbs_ng %in% c(1,2) ~ 1,
                             reduchbs_ng %in% c(3,4) ~ 2,
                             reduchbs_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         simpletransfus_ng = case_when(simpletransfus_ng %in% c(1,2) ~ 1,
                             simpletransfus_ng %in% c(3,4) ~ 2,
                             simpletransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         theratransfus_ng = case_when(theratransfus_ng %in% c(1,2) ~ 1,
                             theratransfus_ng %in% c(3,4) ~ 2,
                             theratransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         delaytransfus_ng = case_when(delaytransfus_ng %in% c(1,2) ~ 1,
                             delaytransfus_ng %in% c(3,4) ~ 2,
                             delaytransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         ipptransfus_ng = case_when(ipptransfus_ng %in% c(1,2) ~ 1,
                             ipptransfus_ng %in% c(3,4) ~ 2,
                             ipptransfus_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         rbcantigen_ng = case_when(rbcantigen_ng %in% c(1,2) ~ 1,
                             rbcantigen_ng %in% c(3,4) ~ 2,
                             rbcantigen_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         leukreduc_ng = case_when(leukreduc_ng %in% c(1,2) ~ 1,
                             leukreduc_ng %in% c(3,4) ~ 2,
                             leukreduc_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         chelatthera_ng = case_when(chelatthera_ng %in% c(1,2) ~ 1,
                             chelatthera_ng %in% c(3,4) ~ 2,
                             chelatthera_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         proteinuria_ng = case_when(proteinuria_ng %in% c(1,2) ~ 1,
                             proteinuria_ng %in% c(3,4) ~ 2,
                             proteinuria_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         htn_ng = case_when(htn_ng %in% c(1,2) ~ 1,
                             htn_ng %in% c(3,4) ~ 2,
                             htn_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         bpchild_ng = case_when(bpchild_ng %in% c(1,2) ~ 1,
                             bpchild_ng %in% c(3,4) ~ 2,
                             bpchild_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         extremities_ng = case_when(extremities_ng %in% c(1,2) ~ 1,
                             extremities_ng %in% c(3,4) ~ 2,
                             extremities_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         transcdop_ng = case_when(transcdop_ng %in% c(1,2) ~ 1,
                             transcdop_ng %in% c(3,4) ~ 2,
                             transcdop_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assessresp_ng = case_when(assessresp_ng %in% c(1,2) ~ 1,
                             assessresp_ng %in% c(3,4) ~ 2,
                             assessresp_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         reproriskasses_ng = case_when(reproriskasses_ng %in% c(1,2) ~ 1,
                             reproriskasses_ng %in% c(3,4) ~ 2,
                             reproriskasses_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         adultscdscreen_ng = case_when(adultscdscreen_ng %in% c(1,2) ~ 1,
                             adultscdscreen_ng %in% c(3,4) ~ 2,
                             adultscdscreen_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assessavn_ng = case_when(assessavn_ng %in% c(1,2) ~ 1,
                             assessavn_ng %in% c(3,4) ~ 2,
                             assessavn_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         pregtransfuse_ng = case_when(pregtransfuse_ng %in% c(1,2) ~ 1,
                             pregtransfuse_ng %in% c(3,4) ~ 2,
                             pregtransfuse_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         assesssleepbreath_ng = case_when(assesssleepbreath_ng %in% c(1,2) ~ 1,
                             assesssleepbreath_ng %in% c(3,4) ~ 2,
                             assesssleepbreath_ng == 5 ~ 3,
                             TRUE ~ NA
                             ),
         specialist_ng = case_when(specialist_ng %in% c(1,2) ~ 1,
                             specialist_ng %in% c(3,4) ~ 2,
                             specialist_ng == 5 ~ 3,
                             TRUE ~ NA
                             ))
```

### transfus10_ng	

```{r}
binary_adh %>% 
  group_by(transfus10_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


### reduchbs_ng - Provide prophylactic blood transfusions for maximum reduction of hemoglobin S (< 30%) in individuals with HbSS	

```{r}
binary_adh %>% 
  group_by(reduchbs_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### simpletransfus_ng - Order simple transfusion for uncomplicated vaso-occlusive episode	

```{r}
binary_adh %>% 
  group_by(simpletransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### theratransfus_ng - Provide therapeutic blood transfusions for acute sickle cell disease complications	

```{r}
binary_adh %>% 
  group_by(theratransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### delaytransfus_ng - Delay transfusion while seeking cause of acute, severe anemia	

```{r}
binary_adh %>% 
  group_by(delaytransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### ipptransfus_ng - Create an individualized patient plan for the use of simple and/or exchange transfusion as part of disease management	

```{r}
binary_adh %>% 
  group_by(ipptransfus_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### rbcantigen_ng - Match for minor red blood cell antigens 

```{r}
binary_adh %>% 
  group_by(rbcantigen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### leukreduc_ng - Use pre-storage leukoreduction or bedside white blood cell filtration

```{r}
binary_adh %>% 
  group_by(leukreduc_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### chelatthera_ng - Order chelation therapy

```{r}
binary_adh %>% 
  group_by(chelatthera_ng) %>% 
  summarise(
    n = n()
  ) %>% 
 mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```


## Table 4d (binary).  Healthcare Provider Adherence to screening recommendations

### proteinuria_ng

```{r}
binary_adh %>% 
  group_by(proteinuria_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### htn_ng - Screen for hypertension in adults (SBP≥130, DBP≥80)

```{r}
binary_adh %>% 
  group_by(htn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### bpchild_ng - Monitor BP in children

```{r}
binary_adh %>% 
  group_by(bpchild_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### extremities_ng - Examine extremities and initiate treatment for active or healed ulcers

```{r}
binary_adh %>% 
  group_by(extremities_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### transcdop_ng - Conduct annual transcranial doppler from ages 2 to 16 years according to STOP study methods (specific to HbSS, HbSβ0 thalassemia) 

```{r}
binary_adh %>% 
  group_by(transcdop_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assessresp_ng - Assess for signs and symptoms of respiratory problems like asthma, COPD, restrictive lung disease or refer to an appropriate specialist

```{r}
binary_adh %>% 
  group_by(assessresp_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### reproriskasses_ng - Conduct reproductive risk assessment, educational and health promotion counseling or refer to specialist for women and men of childbearing age or refer to an appropriate specialist 

```{r}
binary_adh %>% 
  group_by(reproriskasses_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### adultscdscreen_ng - Refer male and female partners for sickle cell screening 

```{r}
binary_adh %>% 
  group_by(adultscdscreen_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assessavn_ng - Screen all individuals with SCD and intermittent or chronic hip pain for avascular necrosis (history, physical exam, imaging) 

```{r}
binary_adh %>% 
  group_by(assessavn_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### pregtransfuse_ng - Screen women who have been transfused and are pregnant for red cell alloantibodies 

```{r}
binary_adh %>% 
  group_by(pregtransfuse_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### assesssleepbreath_ng - Assess for signs and symptoms of sleep-disordered breathing like sleep apnea or refer to an appropriate specialist 

```{r}
binary_adh %>% 
  group_by(assesssleepbreath_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```

### specialist_ng - Refer to appropriate specialist for specific disease complication or co-morbidity treatment

```{r}
binary_adh %>% 
  group_by(specialist_ng) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    total = sum(n),
    percentage = round(n/sum(n)*100,1)
  )
```








