---
title: "Supple_table 2_EXTENDaim1"
author: "Wai"
date: "2024-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

# Importing datasets

## This dataset "data/SCDKAPAim1.csv" is an clean one dated Feb 9,2024, created by Kirstin. 
## Changes by March 19, 2024: Feb_20_2024_SCDKAPAim1 is the updated dataset that includes all required variables. Hence, this dataset will be used for the following data analysis. Previously, left_join function was used to join the datasets but it will not be applied anymore.

```{r}
SCDKAPa1 <- read_csv("data/Feb_20_2024_SCDKAPAim1.csv")
```
## This dataset "data/SCDKAPAll.csv" is downloaded by Dr. Ibemere to add addtional variables, particularly (other_ng and other_fluid_ng) to the above dataset. 

```{r}
#SCDKAPAll <- read_csv("data/SCDKAPAll.csv") #this dataset "Feb_20_2024_SCDKAPAim1.csv" already joined the required variables.
```
# Joining dataset for other_ng and other_fluid_ng variables

## First, will narrow down the variabbles (other_ng and other_fluid_ng) from overall dataset

```{r}

#SCDKAPAll_2 <- SCDKAPAll %>% 
  #select(record_id, other_ng, other_fluid_ng)
```

## Second, join the dataset by using left_join function

```{r}
#SCDKAPAim1_tbl2 <- SCDKAPAim1 %>% 
  #left_join(SCDKAPAll_2, join_by(record_id))
```

## Third, integrating some observations of other_ng + other_fluid_ng to respective main category

* 5% dextrose water at 1.5 maintenance to Isotonic Crystalloid at maintenance rate as suggested by Dr. Ibemere


```{r}
SCDKAPa1 %>% 
  select(record_id, isocrysmain_ng, other_ng) %>% 
  filter(record_id %in% c(26, 43, 54, 417, 225))
```

* observation 225 responded in both variables (isocrysmain_ng and other_ng) and hence, we will use both responses in calculation of percentage for each variable


### Integrating values of selected observations from other_ng to isocrysmain_ng and then create updated dataset

```{r}
SCDKAPa1 <- SCDKAPa1 %>%
  mutate(
    isocrysmain_ng = ifelse(record_id %in% c(26, 43, 54, 417), other_ng, isocrysmain_ng),
    other_ng = ifelse(record_id %in% c(26, 43, 54, 417), NA, other_ng)
  )
```

### checking the integration is functional or not

```{r}
SCDKAPa1 %>%
  filter(record_id %in% c(26, 43, 54, 417, 225)) %>% 
  select(isocrysmain_ng, other_ng)
```

Now we got new dataset for all variables that we need for supplementary table 2.


# Calculating for supplementary table (2) EXTEND Aim 1: Healthcare Provider Choice of Fluid and Frequency of Use for the Treatment of SCD Pain 

## Frequency category: (1) Never, (2) Rarely, (3) Frequently, (4) Always

### Isotonic Crystalloid Bolus

```{r}
isocrysbol_ng1 <- SCDKAPa1 %>% 
  filter(isocrysbol_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, isocrysbol_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[isocrysbol_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[isocrysbol_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(isocrysbol_ng %in% c(1, 2, 3, 4))
 
print(isocrysbol_ng1) 
  
```

```{r}

isocrysbol_ng2 <- SCDKAPa1 %>% 
  filter(isocrysbol_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(isocrysbol_ng == 2), 
            count_3 = sum(isocrysbol_ng == 3), 
            count_4 = sum(isocrysbol_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 186 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1), 
         percent_4 = round(count_4 / total_participants * 100,1))

isocrysbol_ng2
```

### Isotonic Crystalloid at maintenance rate 

```{r}
isocrysmain_ng1 <- SCDKAPa1 %>% 
  filter(isocrysmain_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, isocrysmain_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[isocrysmain_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[isocrysmain_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(isocrysmain_ng %in% c(1, 2, 3, 4)) 
 
print(isocrysmain_ng1) 

```

```{r}
isocrysmain_ng2 <- SCDKAPa1 %>% 
  filter(isocrysmain_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(isocrysmain_ng == 2), 
            count_3 = sum(isocrysmain_ng == 3), 
            count_4 = sum(isocrysmain_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 173 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1),
         percent_4 = round(count_4 / total_participants * 100,1))

isocrysmain_ng2
```

### Isotonic Crystalloid at half-maintenance rate 

```{r}
isocysthalf_ng1 <- SCDKAPa1 %>% 
  filter(isocysthalf_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, isocysthalf_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[isocysthalf_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[isocysthalf_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(isocysthalf_ng %in% c(1, 2, 3, 4)) 
 
print(isocysthalf_ng1) 
```

```{r}
isocysthalf_ng2 <- SCDKAPa1 %>% 
  filter(isocysthalf_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(isocysthalf_ng == 2), 
            count_3 = sum(isocysthalf_ng == 3), 
            count_4 = sum(isocysthalf_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 152 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1), 
         percent_4 = round(count_4 / total_participants * 100,1))

isocysthalf_ng2
```

### Hypotonic fluid at maintenance rate 

```{r}
hypomain_ng1 <- SCDKAPa1 %>% 
  filter(hypomain_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, hypomain_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[hypomain_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[hypomain_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(hypomain_ng %in% c(1, 2, 3, 4)) 
 
print(hypomain_ng1) 
```

```{r}
hypomain_ng2 <- SCDKAPa1 %>% 
  filter(hypomain_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(hypomain_ng == 2), 
            count_3 = sum(hypomain_ng == 3), 
            count_4 = sum(hypomain_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 171 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1),
         percent_4 = round(count_4 / total_participants * 100,1))

hypomain_ng2
```

### Hypotonic fluid at half-maintenance rate 

```{r}
hypohalf_ng1 <- SCDKAPa1 %>% 
  filter(hypohalf_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, hypohalf_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[hypohalf_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[hypohalf_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(hypohalf_ng %in% c(1, 2, 3, 4)) 
 
print(hypohalf_ng1) 
```

```{r}
hypohalf_ng2 <- SCDKAPa1 %>% 
  filter(hypohalf_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(hypohalf_ng == 2), 
            count_3 = sum(hypohalf_ng == 3), 
            count_4 = sum(hypohalf_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 156 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1),
         percent_4 = round(count_4 / total_participants * 100,1))

hypohalf_ng2
```

### Oral hydration (e.g. water and/or ORS by mouth) 

```{r}
oralhydra_ng1 <- SCDKAPa1 %>% 
  filter(oralhydra_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, oralhydra_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[oralhydra_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[oralhydra_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1), 
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(oralhydra_ng %in% c(1, 2, 3, 4)) 
 
print(oralhydra_ng1) 
```

```{r}
oralhydra_ng2 <- SCDKAPa1 %>% 
  filter(oralhydra_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(oralhydra_ng == 2), 
            count_3 = sum(oralhydra_ng == 3), 
            count_4 = sum(oralhydra_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 184 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1), 
         percent_4 = round(count_4 / total_participants * 100,1))

oralhydra_ng2
```

### Other 

```{r}
other_ng1 <- SCDKAPa1 %>% 
  filter(other_ng %in% c(1, 2, 3, 4)) %>% 
  group_by(profession_ng_up, other_ng) %>% 
  summarise(count = n(), .groups = 'drop') %>% 
  group_by(profession_ng_up) %>% 
  mutate(total = sum(count)) %>% 
  mutate(percent = round(count / total * 100,1)) %>% 
  mutate(totalreportinguse = sum(count[other_ng %in% c(2, 3, 4)]), 
       totalnouse = sum(count[other_ng == 1]), 
       totalpart = sum(count), 
       percentwuse = round(totalreportinguse / totalpart * 100,1),
       percentwoutuse = round(totalnouse / totalpart * 100,1)) %>% 
  filter(other_ng %in% c(1, 2, 3, 4)) 
 
print(other_ng1) 
```

```{r}
other_ng2 <- SCDKAPa1 %>% 
  filter(other_ng %in% c(2, 3, 4)) %>% 
  summarise(count_2 = sum(other_ng == 2), 
            count_3 = sum(other_ng == 3), 
            count_4 = sum(other_ng == 4), 
            total_participants = n()) %>% 
  mutate(total_percent = round((count_2 + count_3 + count_4) / 67 * 100,1), 
         percent_2 = round(count_2 / total_participants * 100,1), 
         percent_3 = round(count_3 / total_participants * 100,1), 
         percent_4 = round(count_4 / total_participants * 100,1))

other_ng2
```















